---
title: "Antigen Tracking Figures"
author: "Ryan Sheridan"
date: "`r Sys.Date()`"

output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    df_print: "paged"
    code_folding: "hide"
    self_contained: true
    highlight: "kate"
    
params:
  template_dir: "src"
  rds_dir: "sobjs/so"
  p_val_xlsx: "results/figures/figure_3_pvals.xlsx"
  
  # These parameters specify the input Seurat objects and cell types that should be used for analysis
  # sobj_in: Seurat object from Shannon containing CD45- and CD45+ cells for the timepoint. This object is
  # divided based on CD45+/- and the provided cell type.
  # sobj_out: The output Seurat object that is saved after dividing based on CD45+/- and cell type.
  # cell_type: Cell type used for dividing Seurat objects. These labels are matched with the "cell_type1" column.
  # Subtypes from the "cell_type2" column are also removed if they contain <15 cells.
  # title: Plot title
  sobjs:
    value:
      d2_DC:
        sobj_in:   "d2_so.rds"
        sobj_out:  "d2_DC_so_2.rds"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 2)"
      d14_DC:
        sobj_in:   "d14_so.rds"
        sobj_out:  "d14_DC_so_2.rds"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 14)"
      d2_LEC:
        sobj_in:   "d2_so.rds"
        sobj_out:  "d2_LEC_so_2.rds"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 2)"
      d14_LEC:
        sobj_in:   "d14_so.rds"
        sobj_out:  "d14_LEC_so_2.rds"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 14)"
      d2_FRC:
        sobj_in:   "d2_so.rds"
        sobj_out:  "d2_FRC_so_2.rds"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 2)"
      d14_FRC:
        sobj_in:   "d14_so.rds"
        sobj_out:  "d14_FRC_so_2.rds"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 14)"
        
  # These parameters specify paths to clustifyr references for each cell_type provided above
  sobj_refs:
    value:
      LEC: "ref/ref_LEC_xiang.rda"
---

---

`r knitr::knit_child(here::here(params$template_dir, "setup.Rmd"))`

```{r "Plotting functions", echo = F}

# Add one to variable
plus_one <- function(x, n = 1) {
  cmd <- str_c(x, " <<- ", x, " + ", n)
  
  eval(parse(text = cmd))
  eval(parse(text = x))
}

# Add arrows to axis
add_arrow_axis <- function(gg_in, fract = 0.1, ...) {
  
  get_line_coords <- function(range_in, fract) {
    mn  <- range_in[1]
    mx  <- range_in[2]
    dif <- mx - mn

    res <- c(mn - (dif * 0.05), mn + (dif * fract))

    res
  }
  
  x_coords <- ggplot_build(gg_in)$layout$panel_scales_x[[1]]$range$range %>%
    get_line_coords(fract = fract)

  y_coords <- ggplot_build(gg_in)$layout$panel_scales_y[[1]]$range$range %>%
    get_line_coords(fract = fract)
   
  res <- gg_in +
    geom_segment(
      x        = x_coords[1],
      xend     = x_coords[2], 
      y        = y_coords[1], 
      yend     = y_coords[1],
      size     = 0.25,
      color    = "black",
      linejoin = "bevel",
      arrow    = arrow(ends = "last", type = "open", length = unit(0.02, "npc")),
      ...
    ) +
    geom_segment(
      y        = y_coords[1], 
      yend     = y_coords[2], 
      x        = x_coords[1], 
      xend     = x_coords[1], 
      size     = 0.25,
      color    = "black",
      linejoin = "bevel",
      arrow    = arrow(ends = "last", type = "open", length = unit(0.02, "npc")),
      ...
    ) +
    theme(axis.title = element_text(hjust = 0, size = 10))
  
  res
}

# Set equal x-axis scales
equalize_x <- function(gg_list_in, log_tran = T, ...) {
  
  set_lims <- function(gg_in, min_x, max_x, log_tran, ...) {
    res <- gg_in +
      coord_cartesian(xlim = c(min_x, max_x))
    
    if (log_tran) {
      res <- res +
        scale_x_log10(labels = trans_format("log10", math_format(10^.x)), ...)
    }
    
    res
  }
  
  gg_ranges <- gg_list_in %>%
    map(~ ggplot_build(.x)$layout$panel_scales_x[[1]]$range$range)
  
  min_val <- gg_ranges %>%
    map_dbl(~ .x[1]) %>%
    min()
  
  max_val <- gg_ranges %>%
    map_dbl(~ .x[2]) %>%
    max()
  
  res <- gg_list_in %>%
    map(
      set_lims,
      min_x    = min_val, 
      max_x    = max_val, 
      log_tran = log_tran,
      ...
    )
  
  res
}

# Function to create figure panel
create_fig3 <- function(sobj_in, cols_in, subtype_column = "subtype", data_slot = "counts",
                        box_counts = c("Relative ova signal" = "ova_fc"), umap_counts = c("ova counts" = "adt_ovalbumin"), 
                        plot_title = NULL, arrow_axis = F, pt_size = 0.1, pt_outline = 0.4, pt_size_2 = 0.3, pt_outline_2 = 0.5,
                        umap_cell_count = F, box_cell_count = T, control_types = c("B Cell", "T Cell"), ...) {
  
  box_column <- umap_column <- "cell_type"
  box_cols <- umap_cols <- cols_in
  
  # Fetch plotting data
  data_df <- sobj_in %>%
    FetchData(c(subtype_column, box_counts, umap_counts, "UMAP_1", "UMAP_2"), slot = data_slot) %>%
    as_tibble(rownames = "cell_id")
  
  # Add pseudo count
  if (0 %in% pull(data_df, box_counts)) {
    data_df <- data_df %>%
      mutate(
        pseudo = ifelse(!!sym(box_counts) > 0, !!sym(box_counts), NA),
        pseudo = min(pseudo, na.rm = T) * 0.5,
        !!sym(box_counts) := !!sym(box_counts) + pseudo
      )
  }
  
  if (!is.null(names(box_counts))) {
    data_df <- data_df %>%
      rename(!!box_counts)
    
    box_counts <- names(box_counts)
  }
  
  if (!is.null(names(umap_counts))) {
    data_df <- data_df %>%
      rename(!!umap_counts)
    
    umap_counts <- names(umap_counts)
  }
  
  # Set subtype order
  # Move select cell types to front of order
  data_df <- data_df %>%
    mutate(
      cell_type = !!sym(subtype_column),
      cell_type = fct_reorder(cell_type, !!sym(box_counts), median)
    )
  
  type_order <- levels(data_df$cell_type)
  
  if (!is.null(control_types)) {
    control_types <- control_types[control_types %in% type_order]
    type_order <- type_order[!type_order %in% control_types]
    type_order <- c(control_types, type_order)
  }
  
  # Count cells for each subtype
  data_df <- data_df %>%
    group_by(cell_type) %>%
    mutate(cell_count = n_distinct(cell_id)) %>%
    ungroup() %>%
    mutate(cell_type = fct_relevel(cell_type, type_order)) %>%
    arrange(cell_type) %>%
    mutate(
      cell_count = str_c(cell_type, "\n(n = ", cell_count, ")"),
      cell_count = fct_inorder(cell_count)
    )
  
  # Set cell type colors
  names(type_order) <- levels(data_df$cell_count)
  
  cols_df <- tibble(
    cell_type = type_order,
    cell_count = names(type_order)
  )
  
  cols_df <- cols_df %>%
    mutate(color = cols_in[cell_type])
  
  # Subtype UMAP
  if (umap_cell_count) {
    umap_column <- "cell_count"
    umap_cols <- setNames(cols_df$color, cols_df$cell_count)
  }
  
  umap <- data_df %>%
    plot_features(
      feature     = umap_column,
      pt_size     = pt_size,
      pt_outline  = pt_outline,
      plot_cols   = umap_cols,
      feat_levels = rev(names(umap_cols))
    ) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    ggtitle(plot_title) +
    blank_theme +
    theme(
      plot.title = element_text(size = 12),
      legend.position = "none"
    ) +
    theme(...)
  
  if (arrow_axis) {
    umap <- add_arrow_axis(umap)
  }
  
  # OVA UMAP
  if (!is.null(umap_counts)) {
    ova_umap <- data_df %>%
      plot_features(
        feature    = umap_counts,
        plot_cols  = c("#fafafa", "#d7301f"),
        pt_size    = pt_size_2,
        pt_outline = pt_outline_2,
        min_pct    = 0.01,
        max_pct    = 0.99
      ) +
      blank_theme +
      theme(
        plot.title        = element_text(size = 10, hjust = 0.5),
        legend.position   = "right",
        legend.key.width  = unit(0.15, "cm"),
        legend.key.height = unit(0.30, "cm"),
        legend.title      = element_text(size = 10),
        legend.text       = element_text(size = 10)
      )
    
    if (arrow_axis) {
      ova_umap <- add_arrow_axis(ova_umap)
    }
  }
  
  # OVA boxes
  if (box_cell_count) {
    box_column <- "cell_count"
    box_cols <- setNames(cols_df$color, cols_df$cell_count)
  }
  
  boxes <- data_df %>%
    ggplot(aes(!!sym(box_counts), !!sym(box_column), fill = !!sym(box_column))) +
    geom_violin(size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
    stat_summary(geom = "point", color = "black", fun = median) +
    scale_color_manual(values = box_cols) +
    scale_fill_manual(values = box_cols) +
    theme_minimal_vgrid() +
    theme(
      legend.position    = "none",
      axis.title.y       = element_blank(),
      axis.title         = element_text(size = 10),
      axis.text          = element_text(size = 10),
      axis.ticks.x       = element_line(size = 0.1),
      panel.grid.major.x = element_line(size = 0.1)
    )
  
  res <- list(umap, boxes)
  
  if (!is.null(umap_counts)) {
    res <- append(res, list(ova_umap))
  }
  
  names(res) <- rep(plot_title, length(res))
  
  res
}

# Plot correlation
plot_corr <- function(sobj_in, x, y, feat, data_slot, cols_in, plot_title, ...) {
  
  res <- sobj_in %>%
    FetchData(c(x, y, feat), slot = data_slot) %>%
    mutate(
      !!sym(x) := log10(!!sym(x)),
      !!sym(y) := log10(!!sym(y))
    ) %>%
    filter(
      !!sym(x) != -Inf,
      !!sym(y) != -Inf
    ) %>%
    plot_features(
      x         = x,
      y         = y,
      feature   = feat,
      data_slot = "counts",
      plot_cols = cols_in,
      lab_pos   = c(0.9, 1),
      lab_size  = 5,
      calc_cor  = T,
      lm_line   = T,
      ...
    ) +
    ggtitle(plot_title) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    theme_info +
    theme(legend.title = element_blank())
  
  res
}

# Calculate pairwise p-values for gg objects
calc_p_vals <- function(gg_in, sample_name, data_column, type_column, log_tran = T) {
  
  # Pull data from gg object
  gg_data <- gg_in$data
  
  # Log transform
  if (log_tran) {
    gg_data <- gg_data %>%
      mutate(!!sym(data_column) := log10(!!sym(data_column)))
  }
  
  # Calculate median
  gg_stats <- gg_data %>%
    group_by(!!sym(type_column)) %>%
    summarize(med = median(!!sym(data_column)))
  
  # Run wilcox test
  gg_counts <- gg_data %>%
    pull(data_column)
  
  gg_groups <- gg_data %>%
    pull(type_column)
  
  res <- gg_counts %>%
    pairwise.wilcox.test(
      g = gg_groups, 
      p.adj = "bonf"
    ) %>%
    tidy()
  
  # Add medians to data.frame
  res <- gg_stats %>%
    rename(med_1 = med) %>%
    right_join(res, by = c("cell_type" = "group1"))
  
  res <- gg_stats %>%
    rename(med_2 = med) %>%
    right_join(res, by = c("cell_type" = "group2"))
  
  # Format final table
  res <- res %>%
    mutate(Sample = sample_name) %>%
    select(
      Sample,
      `Cell type 1`             = str_c(type_column, ".y"),
      `Median OVA FC 1 (log10)` = med_1,
      `Cell type 2`             = type_column,
      `Median OVA FC 2 (log10)` = med_2,
      p.value
    )
  
  res
}

```

```{r "Setup", echo = F}

# Parameter lists
fig3_names <- c("d2_DC", "d14_DC", "d14_LEC", "d14_FRC")
fig3_sobjs <- sobjs[fig3_names]

fig3_params <- list(
  sobj_in    = fig3_sobjs, 
  plot_title = so_titles[names(fig3_sobjs)],
  cols_in    = so_cols[names(fig3_sobjs)]
)

corr_params <- list(
  sobj_in    = sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

n_plot <- 0

```

```{r, ref.label = c("Plotting functions", "Setup"), eval = F}
```

## Figure 3

```{r, fig.width = 13, fig.height = 18}

# Create panel plots
gg_list <- fig3_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create table of p-values
if (!is.null(params$p_val_xlsx)) {
  p_vals <- gg_list[violin_idx] %>%
    imap(
      calc_p_vals,
      data_column = "Relative ova signal",
      type_column = "cell_type",
      log_tran    = T
    ) %>%
    bind_rows()
  
  p_vals %>%
    write.xlsx(here(params$p_val_xlsx))
}

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Figures for all FRC timepoints

```{r, fig.width = 13, fig.height = 10}

# Figure parameters
FRC_names <- c("d2_FRC", "d14_FRC")
FRC_sobjs <- sobjs[FRC_names]

FRC_params <- list(
  sobj_in      = FRC_sobjs,
  plot_title   = so_titles[names(FRC_sobjs)],
  cols_in      = so_cols[names(FRC_sobjs)],
  pt_size      = c(1.5, 0.1),
  pt_outline   = c(2, 0.4),
  pt_size_2    = c(1.5, 0.3),
  pt_outline_2 = c(2, 0.5)
)

# Create panel plots
gg_list <- FRC_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Clustering for LEC subtype assignment using [Xiang et al.](https://www.frontiersin.org/articles/10.3389/fcvm.2020.00052/full#B40) reference

```{r, fig.width = 18, fig.height = 10}

# Load reference
load(here(params$sobj_refs$LEC))

so_in <- sobjs[["d14_LEC"]] %>%
  FindNeighbors(
    reduction = "pca",
    dims = 1:30
  )

# Get subtypes for different resolutions/thresholds
resln <- c(0.6, 1, 1.4, 1.8, 3)
r <- seq(0.5, 0.8, 0.1)

res_df <- expand.grid(resln, r) %>%
  rename(resln = Var1, r_thresh = Var2) %>%
  as_tibble()

plot_df <- map2(res_df$resln, res_df$r_thresh, ~ {
  res <- so_in %>%
    FindClusters(
      resolution = .x,
      verbose    = F
    ) %>%
    clustify(
      ref_mat     = ref_LEC_xiang,
      cluster_col = "seurat_clusters",
      threshold   = .y
    )
  
  res <- res@meta.data %>%
    as_tibble(rownames = "cell_id") %>%
    mutate(
      subtype  = if_else(cell_type == "LEC", type.clustify, subtype),
      subtype  = str_to_title_v2(subtype),
      UMAP_1   = UMAP_1.x,
      UMAP_2   = UMAP_2.x,
      n_clust  = n_distinct(seurat_clusters),
      r        = r.clustify,
      r_thresh = .y
    ) %>%
    select(
      cell_id, orig.ident, seurat_clusters, 
      cell_type, subtype, n_clust, 
      r, r_thresh, UMAP_1, UMAP_2
    )
  
  res
}) %>%
  bind_rows()

# Subtype UMAPs
subtype_gg <- plot_df %>%
  plot_features(
    feature    = "subtype",
    pt_outline = 0.5,
    pt_size    = 0.05,
    plot_cols  = so_cols[["d14_LEC"]], 
    split_id   = c("n_clust", "r_thresh"), 
    switch     = "y"
  ) +
  blank_theme +
  labs(subtitle = "Clustifyr Threshold", y = "Number of Clusters") +
  guides(color = outline_guide) +
  blank_theme +
  theme(
    plot.subtitle = element_text(hjust = 0.5),
    panel.border  = element_rect(fill = NA, color = "black", size = 0.2),
    legend.title  = element_blank(),
    axis.title.y  = element_text()
  )

# Reference UMAPs
clust_guide <- outline_guide
clust_guide$ncol <- 1

ref_gg <- plot_df %>%
  mutate(r_thresh = "Clusters") %>%
  unique() %>%
  plot_features(
    feature    = "seurat_clusters",
    pt_outline = 0.5,
    pt_size    = 0.05,
    split_id   = c("n_clust", "r_thresh"), 
    switch     = "y"
  ) +
  blank_theme +
  labs(y = "Number of Clusters") +
  guides(fill = clust_guide) +
  blank_theme +
  theme(
    plot.subtitle = element_text(hjust = 0.5),
    panel.border  = element_rect(fill = NA, color = "black", size = 0.2),
    legend.title  = element_blank(),
    axis.title.y  = element_text()
  )

# Correlation UMAPs
cor_df <- plot_df %>%
  mutate(r_thresh = "Correlation") %>%
  unique()

cor_gg <- cor_df %>%
  ggplot(aes(UMAP_1, UMAP_2, color = r))

walk(unique(cor_df$seurat_clusters), ~ {
  pt_1 <- cor_df %>%
    filter(
      seurat_clusters == .x,
      r <= 0.6
    )
  
  pt_2 <- cor_df %>%
    filter(
      seurat_clusters == .x,
      r > 0.6
    )
  
  cor_gg <<- cor_gg +
    geom_point(data = pt_1, color = "black", size = 0.5) +
    geom_point(data = pt_1, color = "white", size = 0.05) +
    geom_point(data = pt_2, color = "black", size = 0.5) +
    geom_point(data = pt_2, size = 0.05)
})

cor_gg <- cor_gg +
  facet_grid(n_clust ~ r_thresh, switch = "y") +
  labs(y = "Number of Clusters") +
  blank_theme +
  theme(
    panel.border = element_rect(fill = NA, color = "black", size = 0.2),
    legend.title = element_blank(),
    axis.title.y = element_text()
  )

# Create final figure
plot_grid(
  ref_gg, cor_gg, subtype_gg,
  rel_widths = c(0.4, 0.4, 1),
  nrow  = 1,
  align = "vh",
  axis  = "tbrl"
)

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Figures for all LEC timepoints

```{r, fig.width = 13, fig.height = 10}

# Figure parameters
LEC_names <- c("d2_LEC", "d14_LEC")
LEC_sobjs <- sobjs[LEC_names]

LEC_params <- list(
  sobj_in      = LEC_sobjs,
  plot_title   = so_titles[names(LEC_sobjs)],
  cols_in      = so_cols[names(LEC_sobjs)],
  pt_size      = c(0.5, 0.1),
  pt_outline   = c(0.8, 0.4),
  pt_size_2    = c(0.5, 0.3),
  pt_outline_2 = c(0.8, 0.5)
)

# Create panel plots
gg_list <- LEC_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Correlation between RNA counts and ova counts grouped by cell type

```{r, fig.width = 15, fig.height = 15}

corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    data_slot = "counts",
    pt_size   = 0.5
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 2,
    align    = "vh",
    axis     = "trbl"
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Correlation between RNA counts and ova counts grouped by cell type and subtype

```{r, fig.width = 20, fig.height = 34}

pad <- c(2, 2, 10.5, 2, 10.5, 2)

corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    split_id  = "subtype",
    data_slot = "counts",
    pt_size   = 1,
    scales    = "free",
    ncol      = 3
  ) %>%
  map2(pad, ~ {
    .x + theme(
      legend.position = "none",
      strip.text      = element_text(size = 14),
      plot.margin     = unit(c(0.2, 0.2, .y, 0.2), "cm")
    )
  }) %>%
  plot_grid(
    plotlist    = .,
    rel_heights = c(1, 1, 1),
    align       = "v",
    ncol        = 2
  )

```

---

<br>

<br>

```{r, fig.width = 15, fig.height = 15, eval = F, echo = F}

# Viccinia genes
vv_genes <- read_tsv(here("ref/VACV_genes.txt"), col_names = "name")

# Matrix sparsity
sobjs %>%
  map_dbl(~ {
    vv_counts <- .x %>%
      GetAssayData(slot = "counts")
    
    vv_counts <- vv_counts[vv_genes$name, ] %>%
      as.matrix()
    
    length(vv_counts[vv_counts == 0]) / length(vv_counts)
  })

# Sum vaccinia counts per cell
vv_sobjs <- sobjs %>%
  map(~ {
    vv_counts <- .x %>%
      GetAssayData(slot = "counts")
    
    vv_counts <- vv_counts[vv_genes$name, ] %>%
      as.matrix() %>%
      colSums()
    
    res <- .x %>%
      AddMetaData(
        metadata = vv_counts,
        col.name = "vv_counts"
      )
    
    res
  })

# Create scatter plots
vv_params <- list(
  sobj_in    = vv_sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

vv_params %>%
  pmap(
    plot_corr,
    x         = c("VV counts (log10)" = "vv_counts"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    data_slot = "counts",
    pt_size   = 0.5
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 2,
    align    = "vh",
    axis     = "trbl"
  )

```


