---
title: "Antigen Tracking Figures"
author: "Ryan Sheridan"
date: "`r Sys.Date()`"

output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    df_print: "paged"
    code_folding: "hide"
    self_contained: true
    highlight: "kate"
    
params:
  template_dir:  "src"
  rds_dir:       "sobjs/so"
  ref_dir:       "ref"
  p_val_xlsx:    "results/figures/figure_3_pvals.xlsx"
  p_max_markers: 0.05                               # Max p-value for marker genes
  FC_min:        0                                  # Min fold change for marker genes
  auc_min:       0.5                                # Min AUC for marker genes
  pct_in_min:    60                                 # Min percentage cells expressing marker in group
  pct_out_max:   100                                # Max percentage cells expressing marker outside group
  uniq_markers:  FALSE                              # Remove markers that are present in more than one group
  
  # These parameters specify the input Seurat objects and cell types that should be used for analysis
  # sobj_in: Seurat object from Shannon containing CD45- and CD45+ cells for the timepoint. This object is
  # divided based on CD45+/- and the provided cell type.
  # sobj_out: The output Seurat object that is saved after dividing based on CD45+/- and cell type.
  # cell_type: Cell type used for dividing Seurat objects. These labels are matched with the "cell_type1" column.
  # Subtypes from the "cell_type2" column are also removed if they contain <15 cells.
  # title: Plot title
  sobjs:
    value:
      d2_DC:
        mat_in:    "results/GEX_CD45pos_d2-ADT_CD45pos_d2/outs/filtered_feature_bc_matrix"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 2)"
        sobj_out:  "d2_DC_so_2.rds"
      d14_DC:
        mat_in:    "results/GEX_CD45pos_d14-ADT_CD45pos_d14/outs/filtered_feature_bc_matrix"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 14)"
        sobj_out:  "d14_DC_so_2.rds"
      d2_LEC:
        mat_in:    "results/GEX_CD45neg_d2-ADT_CD45neg_d2/outs/filtered_feature_bc_matrix"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 2)"
        sobj_out:  "d2_LEC_so_2.rds"
      d14_LEC:
        mat_in:    "results/GEX_CD45neg_d14-ADT_CD45neg_d14/outs/filtered_feature_bc_matrix"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 14)"
        sobj_out:  "d14_LEC_so_2.rds"
      d2_FRC:
        mat_in:    "results/GEX_CD45neg_d2-ADT_CD45neg_d2/outs/filtered_feature_bc_matrix"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 2)"
        sobj_out:  "d2_FRC_so_2.rds"
      d14_FRC:
        mat_in:    "results/GEX_CD45neg_d14-ADT_CD45neg_d14/outs/filtered_feature_bc_matrix"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 14)"
        sobj_out:  "d14_FRC_so_2.rds"
        
  # These parameters specify paths to clustifyr references
  ref_sobjs: ["d2_so.rds", "d14_so.rds"]
  type_ref: "ref_celltype_walsh.rda"
  subtype_refs:
    value:
      DC:         "ref_DC_walsh.rda"
      LEC:        "ref_LEC_xiang.rda"
      fibroblast: "ref_FRC_walsh.rda"
---

---

`r knitr::knit_child(here::here(params$template_dir, "setup.Rmd"))`

```{r "Plotting functions", echo = F}

# Set equal x-axis scales
equalize_x <- function(gg_list_in, log_tran = T, ...) {
  
  set_lims <- function(gg_in, min_x, max_x, log_tran, ...) {
    res <- gg_in +
      coord_cartesian(xlim = c(min_x, max_x))
    
    if (log_tran) {
      res <- res +
        scale_x_log10(labels = trans_format("log10", math_format(10^.x)), ...)
    }
    
    res
  }
  
  gg_ranges <- gg_list_in %>%
    map(~ ggplot_build(.x)$layout$panel_scales_x[[1]]$range$range)
  
  min_val <- gg_ranges %>%
    map_dbl(~ .x[1]) %>%
    min()
  
  max_val <- gg_ranges %>%
    map_dbl(~ .x[2]) %>%
    max()
  
  res <- gg_list_in %>%
    map(
      set_lims,
      min_x    = min_val, 
      max_x    = max_val, 
      log_tran = log_tran,
      breaks   = c(0.01, 1, 100, 10000),
      ...
    )
  
  res
}

# Create figure 3 panels
create_fig3 <- function(sobj_in, cols_in, subtype_column = "subtype", data_slot = "counts", ova_cols = c("#fafafa", "#d7301f"),
                        box_counts = c("Relative ova signal" = "ova_fc"), umap_counts = c("ova counts" = "adt_ovalbumin"), 
                        plot_title = NULL, arrow_axis = F, pt_size = 0.1, pt_outline = 0.4, pt_size_2 = 0.3, pt_outline_2 = 0.5,
                        umap_cell_count = F, box_cell_count = T, control_types = c("B Cell", "T Cell"), ...) {
  
  box_column <- umap_column <- "cell_type"
  box_cols <- umap_cols <- cols_in
  
  # Fetch plotting data
  data_df <- sobj_in %>%
    FetchData(c(subtype_column, box_counts, umap_counts, "UMAP_1", "UMAP_2"), slot = data_slot) %>%
    as_tibble(rownames = "cell_id")
  
  if (!is.null(names(box_counts))) {
    data_df <- data_df %>%
      rename(!!box_counts)
    
    box_counts <- names(box_counts)
  }
  
  if (!is.null(names(umap_counts))) {
    data_df <- data_df %>%
      rename(!!umap_counts)
    
    umap_counts <- names(umap_counts)
  }
  
  # Set subtype order
  # Move select cell types to front of order
  data_df <- data_df %>%
    mutate(
      cell_type = !!sym(subtype_column),
      cell_type = fct_reorder(cell_type, !!sym(box_counts), median)
    )
  
  type_order <- levels(data_df$cell_type)
  
  if (!is.null(control_types)) {
    control_types <- control_types[control_types %in% type_order]
    type_order <- type_order[!type_order %in% control_types]
    type_order <- c(control_types, type_order)
  }
  
  # Count cells for each subtype
  data_df <- data_df %>%
    group_by(cell_type) %>%
    mutate(cell_count = n_distinct(cell_id)) %>%
    ungroup() %>%
    mutate(cell_type = fct_relevel(cell_type, type_order)) %>%
    arrange(cell_type) %>%
    mutate(
      cell_count = str_c(cell_type, "\n(n = ", cell_count, ")"),
      cell_count = fct_inorder(cell_count)
    )
  
  # Set cell type colors
  names(type_order) <- levels(data_df$cell_count)
  
  cols_df <- tibble(
    cell_type = type_order,
    cell_count = names(type_order)
  )
  
  cols_df <- cols_df %>%
    mutate(color = cols_in[cell_type])
  
  # Subtype UMAP
  if (umap_cell_count) {
    umap_column <- "cell_count"
    umap_cols <- setNames(cols_df$color, cols_df$cell_count)
  }
  
  umap <- data_df %>%
    plot_features(
      feature     = umap_column,
      pt_size     = pt_size,
      pt_outline  = pt_outline,
      plot_cols   = umap_cols,
      feat_levels = rev(names(umap_cols))
    ) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    ggtitle(plot_title) +
    blank_theme +
    theme(
      plot.title = element_text(size = 12),
      legend.position = "none"
    ) +
    theme(...)
  
  if (arrow_axis) {
    umap <- add_arrow_axis(umap)
  }
  
  # OVA UMAP
  if (!is.null(umap_counts)) {
    ova_umap <- data_df %>%
      plot_features(
        feature    = umap_counts,
        plot_cols  = ova_cols,
        pt_size    = pt_size_2,
        pt_outline = pt_outline_2,
        min_pct    = 0.01,
        max_pct    = 0.99
      ) +
      blank_theme +
      theme(
        plot.title        = element_text(size = 10, hjust = 0.5),
        legend.position   = "right",
        legend.key.width  = unit(0.15, "cm"),
        legend.key.height = unit(0.30, "cm"),
        legend.title      = element_text(size = 10),
        legend.text       = element_text(size = 10)
      )
    
    if (arrow_axis) {
      ova_umap <- add_arrow_axis(ova_umap)
    }
  }
  
  # OVA boxes
  if (box_cell_count) {
    box_column <- "cell_count"
    box_cols <- setNames(cols_df$color, cols_df$cell_count)
  }
  
  boxes <- data_df %>%
    ggplot(aes(!!sym(box_counts), !!sym(box_column), fill = !!sym(box_column))) +
    geom_violin(size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
    stat_summary(geom = "point", color = "black", fun = median) +
    scale_color_manual(values = box_cols) +
    scale_fill_manual(values = box_cols) +
    theme_minimal_vgrid() +
    theme(
      legend.position    = "none",
      axis.title.y       = element_blank(),
      axis.title         = element_text(size = 10),
      axis.text          = element_text(size = 10),
      axis.ticks.x       = element_line(size = 0.1),
      panel.grid.major.x = element_line(size = 0.1)
    )
  
  res <- list(umap, boxes)
  
  if (!is.null(umap_counts)) {
    res <- append(res, list(ova_umap))
  }
  
  names(res) <- rep(plot_title, length(res))
  
  res
}

# Create figure 4 panels
create_fig4 <- function(sobj_in, ova_cols, feats, feat_cols, ref_cols, pt_size = 0.00001, pt_outline = 0.4, gmm_filt = NULL,
                        low_col = c("white", "white"), sep_bar_labs = F, plot_boxes = T, median_pt = 1) {

  # Theme elements
  legd_guide <- guide_legend(override.aes = list(
    size   = 3.5,
    shape  = 21,
    color  = "black",
    stroke = 0.25
  ))
  
  text_theme <- theme(
    axis.title  = element_text(size = 10),
    legend.text = element_text(size = 8),
    axis.text   = element_text(size = 8)
  )
  
  # Run GMM
  if (!is.null(gmm_filt)) {
    sobj_in <- sobj_in %>%
      classify_ova(
        filt_column = names(gmm_filt), 
        filt        = gmm_filt,
        quiet       = T
      )
  }

  # Data for OVA group UMAP
  ova_order <- names(ova_cols)
  
  data_df <- sobj_in@meta.data %>%
    as_tibble(rownames = "cell_id") %>%
    group_by(GMM_grp) %>%
    mutate(cell_count = n_distinct(cell_id)) %>%
    ungroup() %>%
    mutate(GMM_grp = fct_relevel(GMM_grp, ova_order)) %>%
    arrange(GMM_grp) %>%
    mutate(
      cell_count = str_c(GMM_grp, "\n(n = ", cell_count, ")"),
      cell_count = fct_inorder(cell_count)
    )
  
  # Set OVA group colors
  names(ova_order) <- levels(data_df$cell_count)
  
  cols_df <- tibble(
    grp        = ova_order,
    cell_count = names(ova_order)
  )
  
  cols_df <- cols_df %>%
    mutate(color = ova_cols[grp])
  
  umap_cols <- set_names(
    x  = cols_df$color,
    nm = cols_df$cell_count
  )

  ova_guide <- legd_guide
  ova_guide$reverse <- T
  
  # Create OVA group UMAP
  ova_grp_umap <- data_df %>%
    plot_features(
      feature     = "cell_count",
      pt_size     = pt_size,
      pt_outline  = pt_outline,
      plot_cols   = umap_cols,
      feat_levels = names(ova_order)
    ) +
    guides(color = ova_guide, fill = ova_guide) +
    text_theme +
    blank_theme +
    theme(
      plot.margin     = unit(c(0.2, 1, 0.2, 1.5), "cm"),
      legend.position = "top",
      legend.title    = element_blank(),
      legend.text     = element_text(size = 8)
    )
  
  # OVA hist
  ova_hist <- sobj_in@meta.data %>%
    filter(GMM_grp != "Other") %>%
    mutate(GMM_grp = fct_relevel(GMM_grp, c("ova low", "ova high"))) %>%
    ggplot(aes(adt_ovalbumin, after_stat(density), fill = GMM_grp)) +
    
    stat_density(geom = "point", position = "identity", size = 0, color = "white") +
    geom_density(fill = "white", color = "white", size = 0.3, alpha = 0.9) +
    geom_density(size = 0.3, alpha = 0.8, show.legend = F) +
  
    geom_vline(aes(xintercept = mu), size = 0.5, linetype = 2, color = "grey35") +
    coord_cartesian(ylim = c(0, 1.7)) +
    scale_fill_manual(values = ova_cols) +
    scale_x_log10(labels = trans_format("log10", math_format(10^.x))) +
    labs(x = "ova counts", y = "Density") +
    guides(fill = guide_legend(override.aes = list(shape = 22, size = 3.5, stroke = 0.25, color = "black"))) +
    theme_minimal_hgrid() +
    text_theme +
    theme(
      plot.margin        = unit(c(0.2, 0.5, 0.2, 0.2), "cm"),
      legend.position    = c(0.05, 0.92),
      legend.key.height  = unit(0.15, "cm"),
      legend.title       = element_blank(),
      axis.line.y        = element_line(size = 0.5, color = "grey85"),
      axis.ticks.y       = element_line(size = 0.1),
      panel.grid.major.y = element_line(size = 0.1)
    )
  
  # OVA subtype bar graphs
  type_bar <- sobj_in@meta.data %>%
    as_tibble(rownames = "cell_id") %>%
    mutate(
      subtype = fct_reorder(subtype, cell_id, n_distinct),
      GMM_grp = fct_relevel(GMM_grp, c("ova low", "ova high", "Other"))
    ) %>%
    ggplot(aes(GMM_grp, fill = subtype)) +
    
    stat_count(position = "fill", geom = "point", size = 0, color = "white") +
    geom_bar(position = "fill", size = 0.25, color = "black", show.legend = F) +
    
    scale_fill_manual(values = ref_cols) +
    scale_y_continuous(breaks = c(0, 0.5, 1)) +
    guides(fill = guide_legend(ncol = 1, override.aes = list(shape = 22, size = 3.5, stroke = 0.25, color = "black"))) +
    labs(y = "Fraction of cells") +
    theme_minimal_hgrid() +
    text_theme +
    theme(
      legend.title       = element_blank(),
      legend.key.height  = unit(0.35, "cm"),
      axis.title.x       = element_blank(),
      axis.line.y        = element_line(size = 0.5, color = "grey85"),
      axis.ticks.y       = element_line(size = 0.1),
      panel.grid.major.y = element_blank()
    )
  
  if (sep_bar_labs) {
    type_bar <- type_bar +
      theme(axis.text.x = element_text(hjust = c(0.9, 0.5, 0.1)))
  }
  
  # Reference UMAP
  ref_umap <- sobj_in %>%
    create_ref_umap(
      feature     = "subtype",
      color_guide = legd_guide,
      plot_cols   = ref_cols,
      pt_mtplyr   = pt_size / 0.1,
      pt_outline  = pt_outline
    ) +
    theme(
      plot.margin     = unit(c(0.2, 1.5, 0.2, 0.2), "cm"),
      legend.position = "left",
      legend.margin   = margin(0.2, 0.2, 0.2, 1.5, "cm"),
      legend.text     = element_text(size = 8)
    )
  
  # Create list of feature UMAPs
  feat_umaps <- sobj_in %>%
    create_marker_umaps(
      pt_mtplyr     = pt_size / 0.1,
      add_outline   = pt_outline,
      input_markers = feat_cols,
      low_col       = low_col
    ) %>%
    map(~ {
      .x +
        guides(color = guide_colorbar(frame.colour = "black", frame.linewidth = 0.2)) +
        theme(plot.title = element_text(size = 12))
    })
  
  # Top panel of feature UMAPs
  top_umaps <- append(list(ref_umap), feat_umaps[1:2]) %>%
    plot_grid(
      plotlist   = .,
      rel_widths = c(1, 0.5, 0.5),
      nrow       = 1
    )
  
  # Bottom panel of feature UMAPs
  bot_umaps <- feat_umaps[3:6] %>%
    plot_grid(
      plotlist = .,
      nrow     = 1,
      align    = "h",
      axis     = "tb"
    )
  
  # Final feature UMAP figure
  feat_umaps <- plot_grid(
    top_umaps, bot_umaps,
    ncol  = 1,
    align = "vh",
    axis  = "trbl"
  ) + 
    theme(plot.margin = unit(c(1, 0.2, 1.5, 0.2), "cm"))
  
  # Feature boxplots
  box_data <- sobj_in %>%
    FetchData(c(feats, "subtype", "GMM_grp")) %>%
    as_tibble(rownames = "cell_id") %>%
    pivot_longer(cols = c(-cell_id, -subtype, -GMM_grp)) %>%
    mutate(type_name = str_c(subtype, "_", name)) %>%
    group_by(type_name) %>%
    mutate(up_qt = boxplot.stats(value)$stats[4]) %>%
    ungroup() %>%
    mutate(type_name = fct_reorder(type_name, up_qt, median, .desc = T)) %>%
    group_by(subtype, name) %>%
    mutate(med = median(value)) %>%
    ungroup() %>%
    mutate(name = fct_reorder(name, med, max, .desc = T))
    
  feat_boxes <- box_data %>%
    ggplot(aes(type_name, value, fill = subtype)) +
    facet_wrap(~ name, nrow = 1, scales = "free_x") +
    scale_fill_manual(values = ref_cols) +
    scale_color_manual(values = ref_cols) +
    labs(y = "Counts") +
    theme_minimal_hgrid() +
    text_theme +
    theme(
      strip.text         = element_text(size = 12),
      legend.title       = element_blank(),
      legend.key.height  = unit(0.35, "cm"),
      axis.title.x       = element_blank(),
      axis.text.x        = element_blank(),
      axis.line.x        = element_blank(),
      axis.ticks.x       = element_blank(),
      axis.line.y        = element_line(size = 0.5, color = "grey85"),
      panel.grid.major.y = element_blank(),
      panel.background   = element_rect(fill = "#fafafa")
    )
  
  feat_boxes <- feat_boxes +
    stat_summary(geom = "point", shape = 22, fun = median, size = 0) +
    stat_summary(geom = "point", shape = 22, fun = median, size = median_pt + 1, color = "black") +
    geom_boxplot(
      color          = "white",
      fill           = "white",
      alpha          = 1,
      size           = 0.3,
      width          = 0.6,
      outlier.colour = "white",
      outlier.alpha  = 1,
      outlier.size   = 0.1,
      coef           = 0
    ) +
    geom_boxplot(
      size           = 0.3,
      width          = 0.6,
      outlier.colour = "grey85",
      outlier.alpha  = 1,
      outlier.size   = 0.1,
      show.legend    = F,
      coef           = 0,
      fatten = 0
    ) +
    stat_summary(
      aes(color = subtype),
      geom        = "point",
      shape       = 22,
      fun         = median,
      size        = median_pt,
      stroke      = 1,
      fill        = "white",
      show.legend = F
    ) +
    guides(fill = guide_legend(override.aes = list(size = 3.5, stroke = 0.25)))
  
  # Final top panel
  top_lets <- letters
  bot_lets <- c("", "d", "e")
  
  if (!is.null(gmm_filt)) {
    type_bar <- ggplot() +
      theme_void()
    
    top_lets <- c(letters[1:2], "")
    bot_lets <- c("", "c", "d")
  }
  
  top <- plot_grid(
    ova_grp_umap, ova_hist, type_bar,
    rel_widths     = c(0.86, 1, 0.9),
    labels         = top_lets,
    label_fontface = "plain",
    label_size     = 18,
    align          = "h",
    axis           = "tb",
    nrow           = 1
  )
  
  # Final bottom panel
  blank_gg <- ggplot() +
    theme_void()
  
  bot <- plot_grid(
    feat_boxes, blank_gg,
    rel_widths = c(1, if_else(plot_boxes, 0.45, 0.2))
  )
  
  # Create final figure
  res <- plot_grid(
    top, feat_umaps, feat_boxes,
    rel_heights    = c(0.55, 1.05, 0.35),
    ncol           = 1,
    labels         = bot_lets,
    label_fontface = "plain",
    label_size     = 18
  )
  
  res
}

# Create figure 4 panels
create_fig4_panels <- function(sobj_in, gmm_filt = NULL, genes_in, ref_cols, ova_cols, feat_cols, 
                               low_col = c("white", "white"), sep_bar_labs = F) {
  
  if (!is.null(gmm_filt)) {
    sobj_in <- sobj_in %>%
      classify_ova(
        filt_column = names(gmm_filt),
        filt        = gmm_filt,
        quiet       = T
      )
  }
  
  # Differentially expressed genes for figure
  diff_genes <- sobj_in %>%
    subset(subset = GMM_grp != "Other") %>%
    find_markers(group_column = "GMM_grp") %>%
    filter(group == "ova high") %>%
    arrange(desc(logFC)) %>%
    pull(feature) %>%
    head(24)
  
  n_genes <- 6
  
  feats <- 1:(length(diff_genes) / n_genes) %>%
    map(~ diff_genes[1:n_genes + ((.x - 1) * n_genes)])
  
  feats <- append(list(genes_in), feats)
  
  # Create final figure
  iwalk(feats, ~ {
    umap_cols <- feat_cols[seq_along(.x)]
    umap_cols <- set_names(umap_cols, .x)
    cat("\n### v", .y, "\n", sep = "")
    
    create_fig4(
      sobj_in      = sobj_in, 
      ova_cols     = ova_cols,
      feats        = names(umap_cols),
      feat_cols    = umap_cols,
      ref_cols     = ref_cols,
      low_col      = low_col,
      sep_bar_labs = sep_bar_labs
    ) %>%
      print()
    
    cat("\n\n---\n\n<br>\n\n<br>\n\n")
  })
}

# Plot correlation
plot_corr <- function(sobj_in, x, y, feat, data_slot, cols_in, plot_title, ...) {
  
  res <- sobj_in %>%
    FetchData(c(x, y, feat), slot = data_slot) %>%
    mutate(
      !!sym(x) := log10(!!sym(x)),
      !!sym(y) := log10(!!sym(y))
    ) %>%
    filter(
      !!sym(x) != -Inf,
      !!sym(y) != -Inf
    ) %>%
    plot_features(
      x         = x,
      y         = y,
      feature   = feat,
      data_slot = "counts",
      plot_cols = cols_in,
      lab_pos   = c(0.9, 1),
      lab_size  = 5,
      calc_cor  = T,
      lm_line   = T,
      ...
    ) +
    ggtitle(plot_title) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    theme_info +
    theme(legend.title = element_blank())
  
  res
}

# Calculate pairwise p-values for gg objects
calc_p_vals <- function(gg_in, sample_name, data_column, type_column, log_tran = T) {
  
  # Pull data from gg object
  gg_data <- gg_in$data
  
  # Log transform
  if (log_tran) {
    gg_data <- gg_data %>%
      mutate(!!sym(data_column) := log10(!!sym(data_column)))
  }
  
  # Calculate median
  gg_stats <- gg_data %>%
    group_by(!!sym(type_column)) %>%
    summarize(med = median(!!sym(data_column)))
  
  # Run wilcox test
  gg_counts <- gg_data %>%
    pull(data_column)
  
  gg_groups <- gg_data %>%
    pull(type_column)
  
  res <- gg_counts %>%
    pairwise.wilcox.test(
      g = gg_groups, 
      p.adj = "bonf"
    ) %>%
    tidy()
  
  # Add medians to data.frame
  res <- gg_stats %>%
    rename(med_1 = med) %>%
    right_join(res, by = c("cell_type" = "group1"))
  
  res <- gg_stats %>%
    rename(med_2 = med) %>%
    right_join(res, by = c("cell_type" = "group2"))
  
  # Format final table
  res <- res %>%
    mutate(Sample = sample_name) %>%
    select(
      Sample,
      `Cell type 1`             = str_c(type_column, ".y"),
      `Median OVA FC 1 (log10)` = med_1,
      `Cell type 2`             = type_column,
      `Median OVA FC 2 (log10)` = med_2,
      p.value
    )
  
  res
}

```

```{r "Setup", echo = F}

# Parameter lists
fig3_names <- c("d2_DC", "d14_DC", "d14_LEC", "d14_FRC")
fig3_sobjs <- sobjs[fig3_names]

fig3_params <- list(
  sobj_in    = fig3_sobjs, 
  plot_title = so_titles[names(fig3_sobjs)],
  cols_in    = so_cols[names(fig3_sobjs)]
)

corr_params <- list(
  sobj_in    = sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

n_plot <- 0

```

```{r, ref.label = c("Plotting functions", "Setup"), eval = F}
```

## Figure 3

```{r "Fig 3", fig.width = 13, fig.height = 18}

# Create panel plots
gg_list <- fig3_params %>%
  pmap(
    create_fig3,
    box_counts   = c("Relative ova signal" = "ova_fc"), 
    umap_counts  = c("ova counts" = "adt_ovalbumin"),
    data_slot    = "counts",
    pt_size_2    = 0.1,
    pt_outline_2 = 0.4
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create table of p-values
if (!is.null(params$p_val_xlsx)) {
  p_vals <- gg_list[violin_idx] %>%
    imap(
      calc_p_vals,
      data_column = "Relative ova signal",
      type_column = "cell_type",
      log_tran    = T
    ) %>%
    bind_rows()
  
  p_vals %>%
    write.xlsx(here(params$p_val_xlsx))
}

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Fig 3 - all LECs

Figures for all LEC timepoints

```{r, fig.width = 13, fig.height = 10}

# Figure parameters
LEC_names <- c("d2_LEC", "d14_LEC")
LEC_sobjs <- sobjs[LEC_names]

LEC_params <- list(
  sobj_in      = LEC_sobjs,
  plot_title   = so_titles[names(LEC_sobjs)],
  cols_in      = so_cols[names(LEC_sobjs)],
  pt_size      = c(0.5, 0.1),
  pt_outline   = c(0.8, 0.4),
  pt_size_2    = c(0.5, 0.3),
  pt_outline_2 = c(0.8, 0.5)
)

# Create panel plots
gg_list <- LEC_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Fig 3 - all FRCs

Figures for all FRC timepoints

```{r, fig.width = 13, fig.height = 10}

# Figure parameters
FRC_names <- c("d2_FRC", "d14_FRC")
FRC_sobjs <- sobjs[FRC_names]

FRC_params <- list(
  sobj_in      = FRC_sobjs,
  plot_title   = so_titles[names(FRC_sobjs)],
  cols_in      = so_cols[names(FRC_sobjs)],
  pt_size      = c(1.5, 0.1),
  pt_outline   = c(2, 0.4),
  pt_size_2    = c(1.5, 0.3),
  pt_outline_2 = c(2, 0.5)
)

# Create panel plots
gg_list <- FRC_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Figure 4 {.tabset .tabset-pills}

LEC markers associated with high antigen counts. (a) LECs containing low and high antigen counts were identified using a gaussian mixture model. A UMAP projection is shown for ova-low and ova-high cells. T cells, B cells, and epithelial cells are shown in white (Other). (b) The distribution of ova antigen counts is shown for ova-low and ova-high cells. Dotted lines indicate the mean counts for each population. (c) The fraction of cells belonging to each LEC subtype is shown for ova-low and ova-high populations. (d) Gene expression counts were plotted for select genes associated with ova-high LECs. (e) The expression of ova-high LEC markers is shown for each LEC subtype.  

```{r "Fig 4", fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Prox1", "Cavin1", "Cavin2", "Stab1", "Stab2", "Csf1")

# Seurat object for figure
so_name <- "d14_LEC"

create_fig4_panels(
  sobj_in   = sobjs[[so_name]],
  genes_in  = genes,
  ref_cols  = so_cols[[so_name]],
  ova_cols  = ova_cols,
  feat_cols = feat_cols
)

```

## Fig 4 - day 2 LECs {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Prox1", "Cavin1", "Cavin2", "Stab1", "Stab2", "Csf1")

# Seurat object for figure
so_name <- "d2_LEC"

create_fig4_panels(
  sobj_in   = sobjs[[so_name]],
  genes_in  = genes,
  ref_cols  = so_cols[[so_name]],
  ova_cols  = ova_cols,
  feat_cols = feat_cols
)

```

## Fig 4 - day 2 - cDC2 Tbet- {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Ccl2", "Mif", "Msr1", "Pkm", "Lgals3", "Aif1")

# Seurat object for figure
so_name <- "d2_DC"
type <- "cDC2 Tbet-"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova low", "ova high")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = c("white", "#fafafa"),
  sep_bar_labs = T
)

```

## Fig 4 - day 2 - CCR7hi Mig cDC2 {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Cdc42ep3", "Malt1", "Jak2", "Gpr183", "Tpm1", "Aplp2")

# Seurat object for figure
so_name <- "d2_DC"
type <- "CCR7hi Mig cDC2"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova low", "ova high")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = c("white", "#fafafa"),
  sep_bar_labs = T
)

```

## Fig 4 - day 2 - cDC1 {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Skil", "Ddx3x", "Nrp2", "Fscn1", "Tmem123", "Serpinb9")

# Seurat object for figure
so_name <- "d2_DC"
type <- "cDC1"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova low", "ova high")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = c("white", "#fafafa"),
  sep_bar_labs = T
)

```

## Fig 4 - day 2 - CCR7hi Mig cDC1 {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Sema7a", "Phip", "Cd81", "Cd9", "Ddx6", "Ndrg1")

# Seurat object for figure
so_name <- "d2_DC"
type <- "CCR7hi Mig cDC1"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova high", "ova low")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = c("white", "#fafafa"),
  sep_bar_labs = T
)

```

## Fig 4 - day 14 - cDC2 Tbet- {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Cd53", "Ywhab", "Cdk2ap2", "Sh3bgrl", "Serp1", "Pycard")

# Seurat object for figure
so_name <- "d14_DC"
type <- "cDC2 Tbet-"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova high", "ova low")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = "white",
  sep_bar_labs = T
)

```

## Fig 4 - day 14 - cDC2 Tbet+ {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Siva1", "Rock2", "Dram1", "Dck", "Mat2a", "Larp4b")

# Seurat object for figure
so_name <- "d14_DC"
type <- "cDC2 Tbet+"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova high", "ova low")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = "white",
  sep_bar_labs = T
)

```

## Fig 4 - day 14 - CCR7hi Mig cDC2 {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Insm1", "Cd200", "Poglut1", "Adora2a", "Nupr1", "Tes")

# Seurat object for figure
so_name <- "d14_DC"
type <- "CCR7hi Mig cDC2"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova high", "ova low")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = "white",
  sep_bar_labs = T
)

```

## Fig 4 - day 14 - CCR7hi Mig cDC1 {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Ccl22", "Eps15", "Il21r", "Dynll2", "Ccser2", "Ccng2")

# Seurat object for figure
so_name <- "d14_DC"
type <- "CCR7hi Mig cDC1"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova high", "ova low")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = "white",
  sep_bar_labs = T
)

```

## Fig 4 - day 14 - Nr4a1+SC {.tabset .tabset-pills}

```{r, fig.width = 10, fig.height = 11.5, results = "asis"}

# Genes of interest
genes <- c("Ccl22", "Eps15", "Il21r", "Dynll2", "Ccser2", "Ccng2")

# Seurat object for figure
so_name <- "d14_FRC"
type <- "Nr4a1+SC"

create_fig4_panels(
  sobj_in      = sobjs[[so_name]],
  genes_in     = genes,
  ref_cols     = so_cols[[so_name]],
  ova_cols     = ova_cols[c("Other", "ova high", "ova low")],
  feat_cols    = feat_cols,
  gmm_filt     = c(subtype = type),
  low_col      = "white"
)

```

## Cell type ova correlation

Correlation between RNA counts and ova counts grouped by cell type

```{r, fig.width = 15, fig.height = 15}

corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    data_slot = "counts",
    pt_size   = 0.5
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 2,
    align    = "vh",
    axis     = "trbl"
  )

```

---

<br>

<br>

## Cell subtype ova correlation

Correlation between RNA counts and ova counts grouped by cell type and subtype

```{r, fig.width = 20, fig.height = 34}

pad <- c(2, 2, 10.5, 2, 10.5, 2)

corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    split_id  = "subtype",
    data_slot = "counts",
    pt_size   = 1,
    scales    = "free",
    ncol      = 3
  ) %>%
  map2(pad, ~ {
    .x + theme(
      legend.position = "none",
      strip.text      = element_text(size = 14),
      plot.margin     = unit(c(0.2, 0.2, .y, 0.2), "cm")
    )
  }) %>%
  plot_grid(
    plotlist    = .,
    rel_heights = c(1, 1, 1),
    align       = "v",
    ncol        = 2
  )

```

---

<br>

<br>

```{r, fig.width = 15, fig.height = 15, eval = F, echo = F}

# Viccinia genes
vv_genes <- read_tsv(here("ref/VACV_genes.txt"), col_names = "name")

# Matrix sparsity
sobjs %>%
  map_dbl(~ {
    vv_counts <- .x %>%
      GetAssayData(slot = "counts")
    
    vv_counts <- vv_counts[vv_genes$name, ] %>%
      as.matrix()
    
    length(vv_counts[vv_counts == 0]) / length(vv_counts)
  })

# Sum vaccinia counts per cell
vv_sobjs <- sobjs %>%
  map(~ {
    vv_counts <- .x %>%
      GetAssayData(slot = "counts")
    
    vv_counts <- vv_counts[vv_genes$name, ] %>%
      as.matrix() %>%
      colSums()
    
    res <- .x %>%
      AddMetaData(
        metadata = vv_counts,
        col.name = "vv_counts"
      )
    
    res
  })

# Create scatter plots
vv_params <- list(
  sobj_in    = vv_sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

vv_params %>%
  pmap(
    plot_corr,
    x         = c("VV counts (log10)" = "vv_counts"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    data_slot = "counts",
    pt_size   = 0.5
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 2,
    align    = "vh",
    axis     = "trbl"
  )

```
