---
title: "Antigen Tracking Figures"
author: "Ryan Sheridan"
date: "`r Sys.Date()`"

output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    df_print: "paged"
    code_folding: "hide"
    self_contained: true
    highlight: "kate"
    
params:
  template_dir: "src"
  rds_dir: "sobjs/so"
  p_val_xlsx: "results/figures/figure_3_pvals.xlsx"
  
  # These parameters specify the input Seurat objects and cell types that should be used for analysis
  # sobj_in: Seurat object from Shannon containing CD45- and CD45+ cells for the timepoint. This object is
  # divided based on CD45+/- and the provided cell type.
  # sobj_out: The output Seurat object that is saved after dividing based on CD45+/- and cell type.
  # cell_type: Cell type used for dividing Seurat objects. These labels are matched with the "cell_type1" column.
  # Subtypes from the "cell_type2" column are also removed if they contain <15 cells.
  # title: Plot title
  sobjs:
    value:
      d2_DC:
        sobj_in:   "d2_so.rds"
        sobj_out:  "d2_DC_so_2.rds"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 2)"
      d14_DC:
        sobj_in:   "d14_so.rds"
        sobj_out:  "d14_DC_so_2.rds"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 14)"
      d2_LEC:
        sobj_in:   "d2_so.rds"
        sobj_out:  "d2_LEC_so_2.rds"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 2)"
      d14_LEC:
        sobj_in:   "d14_so.rds"
        sobj_out:  "d14_LEC_so_2.rds"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 14)"
      d2_FRC:
        sobj_in:   "d2_so.rds"
        sobj_out:  "d2_FRC_so_2.rds"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 2)"
      d14_FRC:
        sobj_in:   "d14_so.rds"
        sobj_out:  "d14_FRC_so_2.rds"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 14)"
        
  # These parameters specify paths to clustifyr references for each cell_type provided above
  sobj_refs:
    value:
      LEC: "ref/ref_LEC_xiang.rda"
---

---

`r knitr::knit_child(here::here(params$template_dir, "setup.Rmd"))`

```{r "Plotting functions", echo = F}

# Add one to variable
plus_one <- function(x, n = 1) {
  cmd <- str_c(x, " <<- ", x, " + ", n)
  
  eval(parse(text = cmd))
  eval(parse(text = x))
}

# Add arrows to axis
add_arrow_axis <- function(gg_in, fract = 0.1, ...) {
  
  get_line_coords <- function(range_in, fract) {
    mn  <- range_in[1]
    mx  <- range_in[2]
    dif <- mx - mn

    res <- c(mn - (dif * 0.05), mn + (dif * fract))

    res
  }
  
  x_coords <- ggplot_build(gg_in)$layout$panel_scales_x[[1]]$range$range %>%
    get_line_coords(fract = fract)

  y_coords <- ggplot_build(gg_in)$layout$panel_scales_y[[1]]$range$range %>%
    get_line_coords(fract = fract)
   
  res <- gg_in +
    geom_segment(
      x        = x_coords[1],
      xend     = x_coords[2], 
      y        = y_coords[1], 
      yend     = y_coords[1],
      size     = 0.25,
      color    = "black",
      linejoin = "bevel",
      arrow    = arrow(ends = "last", type = "open", length = unit(0.02, "npc")),
      ...
    ) +
    geom_segment(
      y        = y_coords[1], 
      yend     = y_coords[2], 
      x        = x_coords[1], 
      xend     = x_coords[1], 
      size     = 0.25,
      color    = "black",
      linejoin = "bevel",
      arrow    = arrow(ends = "last", type = "open", length = unit(0.02, "npc")),
      ...
    ) +
    theme(axis.title = element_text(hjust = 0, size = 10))
  
  res
}

# Set equal x-axis scales
equalize_x <- function(gg_list_in, log_tran = T, ...) {
  
  set_lims <- function(gg_in, min_x, max_x, log_tran, ...) {
    res <- gg_in +
      coord_cartesian(xlim = c(min_x, max_x))
    
    if (log_tran) {
      res <- res +
        scale_x_log10(labels = trans_format("log10", math_format(10^.x)), ...)
    }
    
    res
  }
  
  gg_ranges <- gg_list_in %>%
    map(~ ggplot_build(.x)$layout$panel_scales_x[[1]]$range$range)
  
  min_val <- gg_ranges %>%
    map_dbl(~ .x[1]) %>%
    min()
  
  max_val <- gg_ranges %>%
    map_dbl(~ .x[2]) %>%
    max()
  
  res <- gg_list_in %>%
    map(
      set_lims,
      min_x    = min_val, 
      max_x    = max_val, 
      log_tran = log_tran,
      ...
    )
  
  res
}

# Function to create figure panel
create_fig3 <- function(sobj_in, cols_in, subtype_column = "subtype", data_slot = "counts",
                        box_counts = c("Relative ova signal" = "ova_fc"), umap_counts = c("ova counts" = "adt_ovalbumin"), 
                        plot_title = NULL, arrow_axis = F, pt_size = 0.1, pt_outline = 0.4, pt_size_2 = 0.3, pt_outline_2 = 0.5,
                        umap_cell_count = F, box_cell_count = T, control_types = c("B Cell", "T Cell"), ...) {
  
  box_column <- umap_column <- "cell_type"
  box_cols <- umap_cols <- cols_in
  
  # Fetch plotting data
  data_df <- sobj_in %>%
    FetchData(c(subtype_column, box_counts, umap_counts, "UMAP_1", "UMAP_2"), slot = data_slot) %>%
    as_tibble(rownames = "cell_id")
  
  if (!is.null(names(box_counts))) {
    data_df <- data_df %>%
      rename(!!box_counts)
    
    box_counts <- names(box_counts)
  }
  
  if (!is.null(names(umap_counts))) {
    data_df <- data_df %>%
      rename(!!umap_counts)
    
    umap_counts <- names(umap_counts)
  }
  
  # Set subtype order
  # Move select cell types to front of order
  data_df <- data_df %>%
    mutate(
      cell_type = !!sym(subtype_column),
      cell_type = fct_reorder(cell_type, !!sym(box_counts), median)
    )
  
  type_order <- levels(data_df$cell_type)
  
  if (!is.null(control_types)) {
    control_types <- control_types[control_types %in% type_order]
    type_order <- type_order[!type_order %in% control_types]
    type_order <- c(control_types, type_order)
  }
  
  # Count cells for each subtype
  data_df <- data_df %>%
    group_by(cell_type) %>%
    mutate(cell_count = n_distinct(cell_id)) %>%
    ungroup() %>%
    mutate(cell_type = fct_relevel(cell_type, type_order)) %>%
    arrange(cell_type) %>%
    mutate(
      cell_count = str_c(cell_type, "\n(n = ", cell_count, ")"),
      cell_count = fct_inorder(cell_count)
    )
  
  # Set cell type colors
  names(type_order) <- levels(data_df$cell_count)
  
  cols_df <- tibble(
    cell_type = type_order,
    cell_count = names(type_order)
  )
  
  cols_df <- cols_df %>%
    mutate(color = cols_in[cell_type])
  
  # Subtype UMAP
  if (umap_cell_count) {
    umap_column <- "cell_count"
    umap_cols <- setNames(cols_df$color, cols_df$cell_count)
  }
  
  umap <- data_df %>%
    plot_features(
      feature     = umap_column,
      pt_size     = pt_size,
      pt_outline  = pt_outline,
      plot_cols   = umap_cols,
      feat_levels = rev(names(umap_cols))
    ) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    ggtitle(plot_title) +
    blank_theme +
    theme(
      plot.title = element_text(size = 12),
      legend.position = "none"
    ) +
    theme(...)
  
  if (arrow_axis) {
    umap <- add_arrow_axis(umap)
  }
  
  # OVA UMAP
  if (!is.null(umap_counts)) {
    ova_umap <- data_df %>%
      plot_features(
        feature    = umap_counts,
        plot_cols  = c("#fafafa", "#d7301f"),
        pt_size    = pt_size_2,
        pt_outline = pt_outline_2,
        min_pct    = 0.01,
        max_pct    = 0.99
      ) +
      blank_theme +
      theme(
        plot.title        = element_text(size = 10, hjust = 0.5),
        legend.position   = "right",
        legend.key.width  = unit(0.15, "cm"),
        legend.key.height = unit(0.30, "cm"),
        legend.title      = element_text(size = 10),
        legend.text       = element_text(size = 10)
      )
    
    if (arrow_axis) {
      ova_umap <- add_arrow_axis(ova_umap)
    }
  }
  
  # OVA boxes
  if (box_cell_count) {
    box_column <- "cell_count"
    box_cols <- setNames(cols_df$color, cols_df$cell_count)
  }
  
  boxes <- data_df %>%
    ggplot(aes(!!sym(box_counts), !!sym(box_column), fill = !!sym(box_column))) +
    geom_violin(size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
    stat_summary(geom = "point", color = "black", fun = median) +
    scale_color_manual(values = box_cols) +
    scale_fill_manual(values = box_cols) +
    theme_minimal_vgrid() +
    theme(
      legend.position    = "none",
      axis.title.y       = element_blank(),
      axis.title         = element_text(size = 10),
      axis.text          = element_text(size = 10),
      axis.ticks.x       = element_line(size = 0.1),
      panel.grid.major.x = element_line(size = 0.1)
    )
  
  res <- list(umap, boxes)
  
  if (!is.null(umap_counts)) {
    res <- append(res, list(ova_umap))
  }
  
  names(res) <- rep(plot_title, length(res))
  
  res
}

# Plot correlation
plot_corr <- function(sobj_in, x, y, feat, data_slot, cols_in, plot_title, ...) {
  
  res <- sobj_in %>%
    FetchData(c(x, y, feat), slot = data_slot) %>%
    mutate(
      !!sym(x) := log10(!!sym(x)),
      !!sym(y) := log10(!!sym(y))
    ) %>%
    filter(
      !!sym(x) != -Inf,
      !!sym(y) != -Inf
    ) %>%
    plot_features(
      x         = x,
      y         = y,
      feature   = feat,
      data_slot = "counts",
      plot_cols = cols_in,
      lab_pos   = c(0.9, 1),
      lab_size  = 5,
      calc_cor  = T,
      lm_line   = T,
      ...
    ) +
    ggtitle(plot_title) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    theme_info +
    theme(legend.title = element_blank())
  
  res
}

# Calculate pairwise p-values for gg objects
calc_p_vals <- function(gg_in, sample_name, data_column, type_column, log_tran = T) {
  
  # Pull data from gg object
  gg_data <- gg_in$data
  
  # Log transform
  if (log_tran) {
    gg_data <- gg_data %>%
      mutate(!!sym(data_column) := log10(!!sym(data_column)))
  }
  
  # Calculate median
  gg_stats <- gg_data %>%
    group_by(!!sym(type_column)) %>%
    summarize(med = median(!!sym(data_column)))
  
  # Run wilcox test
  gg_counts <- gg_data %>%
    pull(data_column)
  
  gg_groups <- gg_data %>%
    pull(type_column)
  
  res <- gg_counts %>%
    pairwise.wilcox.test(
      g = gg_groups, 
      p.adj = "bonf"
    ) %>%
    tidy()
  
  # Add medians to data.frame
  res <- gg_stats %>%
    rename(med_1 = med) %>%
    right_join(res, by = c("cell_type" = "group1"))
  
  res <- gg_stats %>%
    rename(med_2 = med) %>%
    right_join(res, by = c("cell_type" = "group2"))
  
  # Format final table
  res <- res %>%
    mutate(Sample = sample_name) %>%
    select(
      Sample,
      `Cell type 1`             = str_c(type_column, ".y"),
      `Median OVA FC 1 (log10)` = med_1,
      `Cell type 2`             = type_column,
      `Median OVA FC 2 (log10)` = med_2,
      p.value
    )
  
  res
}

```

```{r "Setup", echo = F}

# Parameter lists
fig3_names <- c("d2_DC", "d14_DC", "d14_LEC", "d14_FRC")
fig3_sobjs <- sobjs[fig3_names]

fig3_params <- list(
  sobj_in    = fig3_sobjs, 
  plot_title = so_titles[names(fig3_sobjs)],
  cols_in    = so_cols[names(fig3_sobjs)]
)

corr_params <- list(
  sobj_in    = sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

n_plot <- 0

```

```{r, ref.label = c("Plotting functions", "Setup"), eval = F}
```

## Figure 3

```{r "Fig 3", fig.width = 13, fig.height = 18}

# Create panel plots
gg_list <- fig3_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create table of p-values
if (!is.null(params$p_val_xlsx)) {
  p_vals <- gg_list[violin_idx] %>%
    imap(
      calc_p_vals,
      data_column = "Relative ova signal",
      type_column = "cell_type",
      log_tran    = T
    ) %>%
    bind_rows()
  
  p_vals %>%
    write.xlsx(here(params$p_val_xlsx))
}

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Figure 4

```{r "Fig 4", fig.width = 8, fig.height = 7, echo = F, include = F}

# d14_LEC Seurat object
so_name <- "d14_LEC"
so_type <- "LEC"
sobj <- sobjs[[so_name]]

# Use GMM to divide subtypes based on OVA signal
gmm_res <- sobj %>%
  subset(cell_type == so_type) %>%
  fit_GMM(data_column = "adt_ovalbumin")

gmm_df <- gmm_res$res %>%
  rownames_to_column("cell_id") %>%
  mutate(
    mu = gmm_res$mu[GMM_grp],
    GMM_grp = str_to_lower(GMM_grp),
    GMM_grp = str_c("ova ", GMM_grp),
  ) %>%
  column_to_rownames("cell_id")

# Add OVA groups to meta.data
sobj <- sobj %>%
  AddMetaData(gmm_df)

sobj@meta.data <- sobj@meta.data %>%
  rownames_to_column("cell_id") %>%
  mutate(
    GMM_grp      = if_else(is.na(GMM_grp), "Other", GMM_grp),
    type_ova_grp = str_c(GMM_grp, "-", subtype)
  ) %>%
  column_to_rownames("cell_id")

# Set OVA colors
ova_cols <- c(
  "ova low"  = "#56B4E9",
  "ova high" = "#d7301f",
  "Other"    = "#ffffff"
)

# OVA group UMAP
umap_guide <- outline_guide
umap_guide$reverse <- T

ova_grp_umap <- sobj %>%
  plot_features(
    feature     = "GMM_grp",
    pt_size     = 0.00001,
    pt_outline  = 0.4,
    plot_cols   = ova_cols,
    feat_levels = c("ova high", "ova low", "Other")
  ) +
  guides(color = umap_guide, fill = umap_guide) +
  blank_theme +
  theme(
    plot.margin = unit(c(0.2, 1, 0.2, 1.5), "cm"),
    legend.position = "top",
    legend.title = element_blank(),
    legend.text  = element_text(size = 8)
  )

# OVA hist
ova_hist <- gmm_df %>%
  mutate(GMM_grp = fct_relevel(GMM_grp, c("ova low", "ova high"))) %>%
  ggplot() +
  geom_density(aes(adt_ovalbumin, after_stat(density), fill = GMM_grp), size = 0.3) +
  geom_vline(xintercept = gmm_df$mu, size = 0.5, linetype = 2, color = "grey35") +
  coord_cartesian(ylim = c(0, 1.7)) +
  scale_fill_manual(values = ova_cols) +
  scale_x_log10() +
  
  labs(x = "ova counts", y = "Density") +
  
  theme_minimal_hgrid() +
  theme(
    plot.margin        = unit(c(0.2, 0.5, 0.2, 0.2), "cm"),
    legend.position    = c(0.05, 0.92),
    legend.title       = element_blank(),
    legend.text        = element_text(size = 8),
    axis.title         = element_text(size = 10),
    axis.text          = element_text(size = 8),
    axis.line.y        = element_line(size = 0.5, color = "grey85"),
    axis.ticks.y       = element_line(size = 0.1),
    panel.grid.major.y = element_line(size = 0.1)
  )

  # theme_info +
  # theme(
  #   plot.title      = element_text(size = 13),
  #   legend.position = c(0.05, 0.92),
  #   legend.title    = element_blank(),
  #   legend.text     = element_text(size = 8),
  #   axis.title      = element_text(size = 12),
  #   axis.text       = element_text(size = 8),
  # )

# OVA subtype bar graphs
type_bar <- sobj %>%
  plot_cell_count(
    group_id    = "GMM_grp",
    group_order = names(ova_cols),
    fill_id     = "subtype",
    bar_line    = 0.25,
    plot_colors = so_cols[[so_name]]
  ) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  guides(fill = guide_legend(ncol = 1)) +
  theme_minimal_hgrid() +
  theme(
    legend.title       = element_blank(),
    legend.text        = element_text(size = 8),
    axis.title.x       = element_blank(),
    axis.title         = element_text(size = 10),
    axis.text          = element_text(size = 8),
    axis.line.y        = element_line(size = 0.5, color = "grey85"),
    axis.ticks.y       = element_line(size = 0.1),
    panel.grid.major.y = element_blank()
  )

  
  # theme(
  #   plot.title      = element_text(size = 13),
  #   legend.title    = element_blank(),
  #   legend.text     = element_text(size = 8),
  #   axis.title      = element_text(size = 12),
  #   axis.title.x    = element_blank(),
  #   axis.text       = element_text(size = 8)
  #   # axis.text.x     = element_text(size = 10),
  #   # axis.text.y     = element_text(size = 8),
  # )

```

```{r "Feature plots", echo = F}

# Feature colors
# feat_cols <- get_cols()[seq_along(feats)]
feats <- c( "Prox1", "Cavin1", "Cavin2", "Stab1", "Stab2", "Csf1")

feat_cols <- set_names(
  x  = get_cols(length(feats)),
  nm = feats
)

# Feature UMAPs
ref_umap <- sobj %>%
  create_ref_umap(
    feature     = "subtype",
    color_guide = outline_guide,
    plot_cols   = so_cols[[so_name]],
    pt_mtplyr   = 0.00001,
    pt_outline  = 0.4
  ) +
  theme(
    legend.position = "left",
    legend.margin   = margin(0.2, 1.1, 0.2, 1.5, "cm"),
    plot.margin     = unit(c(0.2, 1.75, 0.2, 0.2), "cm")
    # axis.line = element_line(size = 0.5)
  )

blank_gg <- ggplot() +
  theme_void()

feat_umaps <- sobj %>%
  create_marker_umaps(
    pt_mtplyr     = 0.00001,
    add_outline   = 0.4,
    input_markers = feat_cols,
    low_col       = "white"
  ) %>%
  map(~ .x + theme(plot.title = element_text(size = 12)))
  # map(~ .x + theme(axis.line = element_line(size = 0.5)))

# top_umaps <- append(list(blank_gg, ref_umap), feat_umaps[1:2]) %>%
top_umaps <- append(list(ref_umap), feat_umaps[1:2]) %>%
  plot_grid(
    plotlist = .,
    # rel_widths = c(0.64, 1.31, 0.99, 0.99),
    rel_widths = c(1.95, 0.99, 0.99),
    nrow  = 1,
    align = "h",
    axis  = "tb"
  )

bot_umaps <- feat_umaps[3:6] %>%
  plot_grid(
    plotlist = .,
    nrow     = 1,
    align    = "h",
    axis     = "tb"
  )

feat_umaps <- plot_grid(
  top_umaps, bot_umaps,
  ncol  = 1,
  align = "vh",
  axis  = "trbl"
) + 
  theme(plot.margin = unit(c(1, 0.2, 1.5, 0.2), "cm"))
  # theme(plot.margin = unit(c(0, 0.2, 0.5, 0.2), "cm"))

# Feature violin plots
box_data <- sobj %>%
  FetchData(c(feats, "GMM_grp")) %>%
  as_tibble(rownames = "cell_id") %>%
  pivot_longer(cols = c(-cell_id, -GMM_grp)) %>%
  filter(GMM_grp != "Other") %>%
  mutate(
    name    = fct_relevel(name, names(feat_cols)),
    GMM_grp = fct_relevel(GMM_grp, c("ova low", "ova high"))
  )

feat_boxes <- box_data %>%
  ggplot(aes(GMM_grp, value, fill = name, alpha = GMM_grp)) +
  geom_violin(scale = "area", size = 0.3, draw_quantiles = c(0.25, 0.75)) +
  stat_summary(geom = "point", color = "black", alpha = 1, fun = median) +
  # stat_summary(fun = "median", geom = "point", shape = 22, size = 1, fill = "white", show.legend = F) +
  facet_wrap(~ name, nrow = 1) +
  scale_fill_manual(values = feat_cols) +
  scale_alpha_manual(values = c(0.35, 0.75)) +
  
  # scale_y_continuous(breaks = seq(0, 10, 2)) +
  
  labs(y = "Counts") +
  theme_minimal_hgrid() +
  theme(
    strip.text         = element_text(size = 12),
    legend.position    = "none",
    axis.title.x       = element_blank(),
    axis.title         = element_text(size = 10),
    axis.text          = element_text(size = 8),
    axis.line.y        = element_line(size = 0.5, color = "grey85"),
    axis.ticks.y       = element_line(size = 0.1),
    panel.grid.major.y = element_line(size = 0.1)
  )

```

```{r "V1", fig.width = 10, fig.height = 11.5, results = "hold"}

top <- plot_grid(
  ova_grp_umap, ova_hist, type_bar,
  rel_widths = c(0.86, 1, 0.9),
  labels = letters,
  label_fontface = "plain",
  label_size = 18,
  align = "h", 
  axis  = "tb",
  nrow  = 1
)

bot <- plot_grid(
  feat_boxes, blank_gg,
  rel_widths = c(1, 0.2)
)

plot_grid(
  top, feat_umaps, bot,
  rel_heights = c(0.5, 1, 0.45),
  ncol  = 1,
  labels = c("", "d", "e"),
  label_fontface = "plain",
  label_size = 18
  # align = "vh",
  # axis  = "trbl"
)



# top <- list(ova_grp_umap, ova_hist, type_bar) %>%
#   wrap_plots(ncol = 3, widths = c(0.9, 1, 0.9)) +
#   plot_annotation(tag_levels = "a") &
#   theme(
#     plot.margin = unit(c(0.2, 0.5, 0.2, 0.2), "cm"),
#   )
# wrap_plots(
#   top, feat_umaps, feat_boxes,
#   ncol = 1, 
#   heights = c(0.5, 1, 0.45)
# ) +
#   plot_annotation(tag_levels = "a") &
#   theme(
#     # plot.margin = unit(c(1, 0, 0, 0.2), "cm"),
#     plot.tag = element_text(size = 24, face = "plain")
#     # plot.tag.position = c(-0.08, 1)
#   )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Clustering for LEC subtype assignment using [Xiang et al.](https://www.frontiersin.org/articles/10.3389/fcvm.2020.00052/full#B40) reference

```{r, fig.width = 18, fig.height = 10}

# Load reference
load(here(params$sobj_refs$LEC))

so_in <- sobjs[["d14_LEC"]]

# Get subtypes for different resolutions/thresholds
reslns <- c(0.6, 1, 1.4, 1.8, 2.2)
r <- seq(0.5, 0.8, 0.1)

res_df <- expand.grid(reslns, r) %>%
  rename(resln = Var1, r_thresh = Var2) %>%
  as_tibble()

plot_df <- map2(res_df$resln, res_df$r_thresh, ~ {
  res <- so_in %>%
    FindClusters(
      resolution = .x,
      verbose    = F
    ) %>%
    clustify(
      ref_mat     = ref_LEC_xiang,
      cluster_col = "seurat_clusters",
      threshold   = .y
    )
  
  res <- res@meta.data %>%
    as_tibble(rownames = "cell_id") %>%
    mutate(
      subtype  = if_else(cell_type == "LEC", type.clustify, subtype),
      subtype  = str_to_title_v2(subtype),
      UMAP_1   = UMAP_1.x,
      UMAP_2   = UMAP_2.x,
      n_clust  = str_c(n_distinct(seurat_clusters), " (", .x, ")"),
      r        = r.clustify,
      r_thresh = .y
    ) %>%
    select(
      cell_id, orig.ident, seurat_clusters, 
      cell_type, subtype, n_clust,
      r, r_thresh, UMAP_1, UMAP_2
    )
  
  res
}) %>%
  bind_rows()

# Subtype UMAPs
subtype_gg <- plot_df %>%
  plot_features(
    feature    = "subtype",
    pt_outline = 0.5,
    pt_size    = 0.05,
    plot_cols  = so_cols[["d14_LEC"]],
    split_id   = c("n_clust", "r_thresh"), 
    switch     = "y"
  ) +
  blank_theme +
  labs(subtitle = "Clustifyr Threshold", y = "Number of Clusters") +
  guides(color = outline_guide) +
  blank_theme +
  theme(
    plot.subtitle = element_text(hjust = 0.5),
    panel.border  = element_rect(fill = NA, color = "black", size = 0.2),
    legend.title  = element_blank(),
    axis.title.y  = element_text()
  )

# Reference UMAPs
clust_guide <- outline_guide
clust_guide$ncol <- 1

ref_gg <- plot_df %>%
  mutate(r_thresh = "Clusters") %>%
  unique() %>%
  plot_features(
    feature    = "seurat_clusters",
    pt_outline = 0.5,
    pt_size    = 0.05,
    split_id   = c("n_clust", "r_thresh"), 
    switch     = "y"
  ) +
  blank_theme +
  labs(y = "Number of Clusters") +
  guides(fill = clust_guide) +
  blank_theme +
  theme(
    plot.subtitle = element_text(hjust = 0.5),
    panel.border  = element_rect(fill = NA, color = "black", size = 0.2),
    legend.title  = element_blank(),
    axis.title.y  = element_text()
  )

# Correlation UMAPs
cor_df <- plot_df %>%
  mutate(r_thresh = "Correlation") %>%
  unique()

cor_gg <- cor_df %>%
  ggplot(aes(UMAP_1, UMAP_2, color = r))

walk(unique(cor_df$seurat_clusters), ~ {
  pt_1 <- cor_df %>%
    filter(
      seurat_clusters == .x,
      r <= 0.6
    )
  
  pt_2 <- cor_df %>%
    filter(
      seurat_clusters == .x,
      r > 0.6
    )
  
  cor_gg <<- cor_gg +
    geom_point(data = pt_1, color = "black", size = 0.5) +
    geom_point(data = pt_1, color = "white", size = 0.05) +
    geom_point(data = pt_2, color = "black", size = 0.5) +
    geom_point(data = pt_2, size = 0.05)
})

cor_gg <- cor_gg +
  facet_grid(n_clust ~ r_thresh, switch = "y") +
  labs(y = "Number of Clusters") +
  blank_theme +
  theme(
    panel.border = element_rect(fill = NA, color = "black", size = 0.2),
    legend.title = element_blank(),
    axis.title.y = element_text()
  )

# Create final figure
plot_grid(
  ref_gg, cor_gg, subtype_gg,
  rel_widths = c(0.4, 0.4, 1),
  nrow  = 1,
  align = "vh",
  axis  = "tbrl"
)

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Figures for all LEC timepoints

```{r, fig.width = 13, fig.height = 10}

# Figure parameters
LEC_names <- c("d2_LEC", "d14_LEC")
LEC_sobjs <- sobjs[LEC_names]

LEC_params <- list(
  sobj_in      = LEC_sobjs,
  plot_title   = so_titles[names(LEC_sobjs)],
  cols_in      = so_cols[names(LEC_sobjs)],
  pt_size      = c(0.5, 0.1),
  pt_outline   = c(0.8, 0.4),
  pt_size_2    = c(0.5, 0.3),
  pt_outline_2 = c(0.8, 0.5)
)

# Create panel plots
gg_list <- LEC_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Figures for all FRC timepoints

```{r, fig.width = 13, fig.height = 10}

# Figure parameters
FRC_names <- c("d2_FRC", "d14_FRC")
FRC_sobjs <- sobjs[FRC_names]

FRC_params <- list(
  sobj_in      = FRC_sobjs,
  plot_title   = so_titles[names(FRC_sobjs)],
  cols_in      = so_cols[names(FRC_sobjs)],
  pt_size      = c(1.5, 0.1),
  pt_outline   = c(2, 0.4),
  pt_size_2    = c(1.5, 0.3),
  pt_outline_2 = c(2, 0.5)
)

# Create panel plots
gg_list <- FRC_params %>%
  pmap(
    create_fig3,
    box_counts  = c("Relative ova signal" = "ova_fc"), 
    umap_counts = c("ova counts" = "adt_ovalbumin"),
    data_slot   = "counts"
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Correlation between RNA counts and ova counts grouped by cell type

```{r, fig.width = 15, fig.height = 15}

corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    data_slot = "counts",
    pt_size   = 0.5
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 2,
    align    = "vh",
    axis     = "trbl"
  )

```

---

<br>

<br>

## Supplemental `r plus_one("n_plot")`

Correlation between RNA counts and ova counts grouped by cell type and subtype

```{r, fig.width = 20, fig.height = 34}

pad <- c(2, 2, 10.5, 2, 10.5, 2)

corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    split_id  = "subtype",
    data_slot = "counts",
    pt_size   = 1,
    scales    = "free",
    ncol      = 3
  ) %>%
  map2(pad, ~ {
    .x + theme(
      legend.position = "none",
      strip.text      = element_text(size = 14),
      plot.margin     = unit(c(0.2, 0.2, .y, 0.2), "cm")
    )
  }) %>%
  plot_grid(
    plotlist    = .,
    rel_heights = c(1, 1, 1),
    align       = "v",
    ncol        = 2
  )

```

---

<br>

<br>

```{r, fig.width = 15, fig.height = 15, eval = F, echo = F}

# Viccinia genes
vv_genes <- read_tsv(here("ref/VACV_genes.txt"), col_names = "name")

# Matrix sparsity
sobjs %>%
  map_dbl(~ {
    vv_counts <- .x %>%
      GetAssayData(slot = "counts")
    
    vv_counts <- vv_counts[vv_genes$name, ] %>%
      as.matrix()
    
    length(vv_counts[vv_counts == 0]) / length(vv_counts)
  })

# Sum vaccinia counts per cell
vv_sobjs <- sobjs %>%
  map(~ {
    vv_counts <- .x %>%
      GetAssayData(slot = "counts")
    
    vv_counts <- vv_counts[vv_genes$name, ] %>%
      as.matrix() %>%
      colSums()
    
    res <- .x %>%
      AddMetaData(
        metadata = vv_counts,
        col.name = "vv_counts"
      )
    
    res
  })

# Create scatter plots
vv_params <- list(
  sobj_in    = vv_sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

vv_params %>%
  pmap(
    plot_corr,
    x         = c("VV counts (log10)" = "vv_counts"),
    y         = c("ova counts (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    data_slot = "counts",
    pt_size   = 0.5
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 2,
    align    = "vh",
    axis     = "trbl"
  )

```


