---
title:  "Antigen Tracking Figures"
author: "Ryan Sheridan"
date:   "`r Sys.Date()`"

output: 
  pdf_document:
    latex_engine: xelatex

documentclass: article
mainfont: DejaVu Sans
geometry: top=0.5in,bottom=0.5in,right=2in,left=2in

params:
  template_dir:  "src"
  rds_dir:       "sobjs/so"
  ref_dir:       "ref"
  p_max_markers: 0.05                               # Max p-value for marker genes
  FC_min:        0.25                               # Min fold change for marker genes
  auc_min:       0.5                                # Min AUC for marker genes
  pct_in_min:    50                                 # Min percentage cells expressing marker in group
  pct_out_max:   100                                # Max percentage cells expressing marker outside group
  uniq_markers:  FALSE                              # Remove markers that are present in more than one group
  
  # These parameters specify the input matrices and cell types that should be used for analysis
  # mat_in: Cellranger output folder.
  # cell_type: Cell type used for subsetting Seurat objects.
  # title: Section title.
  # sobj_out: The output Seurat object that is saved after processing and subsetting based on cell type.
  sobjs:
    value:
      d2_DC:
        mat_in:    "results/GEX_CD45pos_d2-ADT_CD45pos_d2/outs/filtered_feature_bc_matrix"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 2)"
        sobj_out:  "d2_DC_so_2.rds"
      d14_DC:
        mat_in:    "results/GEX_CD45pos_d14-ADT_CD45pos_d14/outs/filtered_feature_bc_matrix"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 14)"
        sobj_out:  "d14_DC_so_2.rds"
      d2_LEC:
        mat_in:    "results/GEX_CD45neg_d2-ADT_CD45neg_d2/outs/filtered_feature_bc_matrix"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 2)"
        sobj_out:  "d2_LEC_so_2.rds"
      d14_LEC:
        mat_in:    "results/GEX_CD45neg_d14-ADT_CD45neg_d14/outs/filtered_feature_bc_matrix"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 14)"
        sobj_out:  "d14_LEC_so_2.rds"
      d2_FRC:
        mat_in:    "results/GEX_CD45neg_d2-ADT_CD45neg_d2/outs/filtered_feature_bc_matrix"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 2)"
        sobj_out:  "d2_FRC_so_2.rds"
      d14_FRC:
        mat_in:    "results/GEX_CD45neg_d14-ADT_CD45neg_d14/outs/filtered_feature_bc_matrix"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 14)"
        sobj_out:  "d14_FRC_so_2.rds"
        
  # These parameters specify paths to clustifyr references
  ref_sobjs: ["d2_so.rds", "d14_so.rds"]
  type_ref:  "ref_celltype_walsh.rda"
  xiang_ref: "ref_LEC_xiang.rda"
  subtype_refs:
    value:
      DC:         "ref_DC_walsh.rda"
      LEC:        "ref_LEC_walsh.rda"
      fibroblast: "ref_FRC_walsh.rda"
---

```{r "Chunk opts", echo = F}

# Default chunk options
knitr::opts_chunk$set(
  message = F,
  warning = F,
  echo    = F
)

```

`r knitr::knit_child(here::here(params$template_dir, "setup.Rmd"))`

```{r "Plotting functions", echo = F}

# Set equal x-axis scales
equalize_x <- function(gg_list_in, log_tran = T, ...) {
  
  set_lims <- function(gg_in, min_x, max_x, log_tran, ...) {
    res <- gg_in +
      coord_cartesian(xlim = c(min_x, max_x))
    
    if (log_tran) {
      res <- res +
        scale_x_log10(labels = trans_format("log10", math_format(10^.x)), ...)
    }
    
    res
  }
  
  gg_ranges <- gg_list_in %>%
    map(~ ggplot_build(.x)$layout$panel_scales_x[[1]]$range$range)
  
  min_val <- gg_ranges %>%
    map_dbl(~ .x[1]) %>%
    min()
  
  max_val <- gg_ranges %>%
    map_dbl(~ .x[2]) %>%
    max()
  
  res <- gg_list_in %>%
    map(
      set_lims,
      min_x    = min_val, 
      max_x    = max_val, 
      log_tran = log_tran,
      breaks   = 10^(-4:4),
      ...
    )
  
  res
}

# Create figure 3 panels
create_fig3 <- function(sobj_in, cols_in, subtype_column = "subtype", data_slot = "counts", ova_cols = c("#fafafa", "#d7301f"),
                        box_counts = c("Relative ova signal" = "ova_fc"), umap_counts = c("ova counts" = "adt_ovalbumin"), 
                        plot_title = NULL, pt_size = 0.1, pt_outline = 0.4, pt_size_2 = 0.3, pt_outline_2 = 0.5, box_cell_count = T,
                        control_types = c("B cell", "T cell"), on_top = NULL, ...) {
  
  box_column <- umap_column <- "cell_type"
  box_cols <- umap_cols <- cols_in
  
  # Fetch plotting data
  data_df <- sobj_in %>%
    FetchData(c(subtype_column, box_counts, umap_counts, "UMAP_1", "UMAP_2"), slot = data_slot) %>%
    as_tibble(rownames = "cell_id")
  
  if (!is.null(names(box_counts))) {
    data_df <- data_df %>%
      rename(!!box_counts)
    
    box_counts <- names(box_counts)
  }
  
  if (!is.null(names(umap_counts))) {
    data_df <- data_df %>%
      rename(!!umap_counts)
    
    umap_counts <- names(umap_counts)
  }
  
  # Set subtype order
  # Move select cell types to front of order
  data_df <- data_df %>%
    mutate(
      cell_type = !!sym(subtype_column),
      cell_type = fct_reorder(cell_type, !!sym(box_counts), median)
    )
  
  type_order <- levels(data_df$cell_type)
  
  if (!is.null(control_types)) {
    control_types <- control_types[control_types %in% type_order]
    type_order <- type_order[!type_order %in% control_types]
    type_order <- c(control_types, type_order)
  }
  
  # Count cells for each subtype
  data_df <- data_df %>%
    group_by(cell_type) %>%
    mutate(cell_count = n_distinct(cell_id)) %>%
    ungroup() %>%
    mutate(cell_type = fct_relevel(cell_type, type_order)) %>%
    arrange(cell_type) %>%
    mutate(
      cell_count = str_c(cell_type, "\n(n = ", cell_count, ")"),
      cell_count = fct_inorder(cell_count)
    )
  
  # Set cell type colors
  names(type_order) <- levels(data_df$cell_count)
  
  cols_df <- tibble(
    cell_type = type_order,
    cell_count = names(type_order)
  )
  
  cols_df <- cols_df %>%
    mutate(color = cols_in[cell_type])
  
  # Subtype UMAP
  # Reorder layers of UMAP
  if (!is.null(on_top)) {
    on_top <- umap_cols[on_top]
    
    umap_cols <- umap_cols[!names(umap_cols) %in% names(on_top)]
    umap_cols <- c(umap_cols, on_top)
  }
  
  umap <- data_df %>%
    plot_features(
      feature     = umap_column,
      pt_size     = pt_size,
      pt_outline  = pt_outline,
      plot_cols   = umap_cols,
      feat_levels = names(umap_cols)
    ) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    ggtitle(plot_title) +
    blank_theme +
    theme(
      plot.title = element_text(size = 12),
      legend.position = "none"
    ) +
    theme(...)
  
  # OVA UMAP
  if (!is.null(umap_counts)) {
    ova_umap <- data_df %>%
      plot_features(
        feature    = umap_counts,
        plot_cols  = ova_cols,
        pt_size    = pt_size_2,
        pt_outline = pt_outline_2,
        min_pct    = 0.01,
        max_pct    = 0.99
      ) +
      guides(color = guide_colorbar(frame.colour = "black", frame.linewidth = 0.2)) +
      blank_theme +
      theme(
        plot.title        = element_text(size = 10, hjust = 0.5),
        legend.position   = "right",
        legend.key.width  = unit(0.15, "cm"),
        legend.key.height = unit(0.30, "cm"),
        legend.title      = element_text(size = 10),
        legend.text       = element_text(size = 8)
      )
  }
  
  # OVA boxes
  if (box_cell_count) {
    box_column <- "cell_count"
    box_cols <- set_names(
      x  = cols_df$color,
      nm = cols_df$cell_count
    )
  }
  
  boxes <- data_df %>%
    ggplot(aes(!!sym(box_counts), !!sym(box_column), fill = !!sym(box_column))) +
    geom_violin(size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
    stat_summary(geom = "point", color = "black", fun = median) +
    scale_color_manual(values = box_cols) +
    scale_fill_manual(values = box_cols) +
    theme_minimal_vgrid() +
    theme(
      legend.position    = "none",
      axis.title.y       = element_blank(),
      axis.title         = element_text(size = 10),
      axis.text          = element_text(size = 8),
      axis.ticks.x       = element_line(size = 0.1),
      panel.grid.major.x = element_line(size = 0.1)
    )
  
  res <- list(umap, boxes)
  
  if (!is.null(umap_counts)) {
    res <- append(res, list(ova_umap))
  }
  
  names(res) <- rep(plot_title, length(res))
  
  res
}

# Create GMM panels
create_gmm_panels <- function(sobj_in, gmm_column = "GMM_grp", ova_cols, bar_cols, pt_size = 0.00001,
                              pt_outline = 0.4, show_bars = T, plot_labs = c(letters[1:3], "")) {
  
  # Theme elements
  legd_guide <- guide_legend(override.aes = list(
    size   = 3.5,
    shape  = 21,
    color  = "black",
    stroke = 0.25
  ))
  
  text_theme <- theme(
    axis.title  = element_text(size = 10),
    legend.text = element_text(size = 8),
    axis.text   = element_text(size = 8)
  )
  
  # Data for OVA group UMAP
  ova_order <- names(ova_cols)
  
  data_df <- sobj_in@meta.data %>%
    as_tibble(rownames = "cell_id") %>%
    group_by(!!sym(gmm_column)) %>%
    mutate(cell_count = n_distinct(cell_id)) %>%
    ungroup() %>%
    mutate(!!sym(gmm_column) := fct_relevel(!!sym(gmm_column), ova_order)) %>%
    arrange(!!sym(gmm_column)) %>%
    mutate(
      cell_count = str_c(!!sym(gmm_column), "\n(n = ", cell_count, ")"),
      cell_count = fct_inorder(cell_count)
    )
  
  # Set OVA group colors
  names(ova_order) <- levels(data_df$cell_count)
  
  cols_df <- tibble(
    grp        = ova_order,
    cell_count = names(ova_order)
  )
  
  cols_df <- cols_df %>%
    mutate(color = ova_cols[grp])
  
  umap_cols <- set_names(
    x  = cols_df$color,
    nm = cols_df$cell_count
  )

  ova_guide <- legd_guide
  ova_guide$reverse <- T
  
  # Create OVA group UMAP
  ova_labeller <- function(labels) {
    labels %>%
      map(str_remove, "^[a-zA-Z0-9 \\-\\+]+-")
  }
  
  ova_grp_umap <- data_df %>%
    plot_features(
      feature     = "cell_count",
      pt_size     = pt_size,
      pt_outline  = pt_outline,
      plot_cols   = umap_cols,
      feat_levels = names(ova_order)
    ) +
    scale_color_manual(values = umap_cols, labels = ova_labeller) +
    scale_fill_manual(values = umap_cols, labels = ova_labeller) +
    guides(color = ova_guide, fill = ova_guide) +
    text_theme +
    blank_theme +
    theme(
      plot.margin     = unit(c(0.2, 1, 0.2, 1.5), "cm"),
      legend.position = "top",
      legend.title    = element_blank(),
      legend.text     = element_text(size = 8)
    )
  
  # OVA hist
  # Add +1 pseudo count to adt_ovalbumin since using log scale
  ova_hist_order <- names(ova_cols) %>%
    grep("ova (low|high)", ., value = T)
  
  ova_hist <- sobj_in@meta.data %>%
    filter(!!sym(gmm_column) != "Other") %>%
    
    group_by(!!sym(gmm_column)) %>%
    mutate(mu = mean(adt_ovalbumin)) %>%
    ungroup() %>%
    
    mutate(!!sym(gmm_column) := fct_relevel(!!sym(gmm_column), ova_hist_order)) %>%
    ggplot(aes(adt_ovalbumin + 1, after_stat(density), fill = !!sym(gmm_column))) +
    
    stat_density(geom = "point", position = "identity", size = 0, color = "white") +
    geom_density(fill = "white", color = "white", size = 0.3, alpha = 0.9) +
    geom_density(size = 0.3, alpha = 0.8, show.legend = F) +
    
    geom_vline(aes(xintercept = mu), size = 0.5, linetype = 2, color = "grey35") +
    coord_cartesian(ylim = c(0, 1.7)) +
    scale_fill_manual(values = ova_cols, labels = ova_labeller) +
    scale_x_log10(labels = trans_format("log10", math_format(10^.x)), breaks = 10^(-4:4)) +
    labs(x = "ova counts + 1", y = "Density") +
    guides(fill = guide_legend(override.aes = list(shape = 22, size = 3.5, stroke = 0.25, color = "black"))) +
    theme_minimal_hgrid() +
    text_theme +
    theme(
      plot.margin        = unit(c(0.2, 0.5, 0.2, 0.2), "cm"),
      legend.position    = c(0.05, 0.92),
      legend.key.height  = unit(0.15, "cm"),
      legend.title       = element_blank(),
      axis.line.y        = element_line(size = 0.5, color = "grey85"),
      axis.ticks.y       = element_line(size = 0.1),
      panel.grid.major.y = element_line(size = 0.1)
    )
  
  # OVA subtype bar graphs
  type_bar <- sobj_in@meta.data %>%
    as_tibble(rownames = "cell_id") %>%
    filter(!!sym(gmm_column) != "Other") %>%
    mutate(
      subtype = fct_reorder(subtype, cell_id, n_distinct),
      !!sym(gmm_column) := fct_relevel(!!sym(gmm_column), c("ova low", "ova high"))
    ) %>%
    ggplot(aes(!!sym(gmm_column), fill = subtype)) +
    
    stat_count(position = "fill", geom = "point", size = 0, color = "white") +
    geom_bar(position = "fill", size = 0.25, color = "black", show.legend = F) +
    
    scale_fill_manual(values = bar_cols) +
    scale_y_continuous(breaks = c(0, 0.5, 1)) +
    guides(fill = guide_legend(ncol = 1, override.aes = list(shape = 22, size = 3.5, stroke = 0.25, color = "black"))) +
    labs(y = "Fraction of cells") +
    theme_minimal_hgrid() +
    text_theme +
    theme(
      legend.title       = element_blank(),
      legend.key.height  = unit(0.35, "cm"),
      axis.title.x       = element_blank(),
      axis.line.y        = element_line(size = 0.5, color = "grey85"),
      axis.ticks.y       = element_line(size = 0.1),
      axis.text.x        = element_text(hjust = c(0.6, 0.4)),
      panel.grid.major.y = element_blank()
    )
  
  # Create final figure
  blank_gg <- ggplot() +
    theme_void()
  
  if (!show_bars) {
    type_bar <- blank_gg
  }
  
  res <- plot_grid(
    ova_grp_umap, ova_hist, type_bar, blank_gg,
    rel_widths     = c(0.86, 1, 0.7, 0.2),
    labels         = plot_labs,
    label_fontface = "plain",
    label_size     = 18,
    align          = "h",
    axis           = "tb",
    nrow           = 1
  )
  
  res
}

# Create feature UMAPs
create_feat_umap_panels <- function(sobj_in, feats, ref_cols, pt_size = 0.00001, pt_outline = 0.4,
                                    low_col = c("white", "white"), high_col_mtplyr = 1, on_top = NULL) {
  
  # Theme elements
  legd_guide <- guide_legend(override.aes = list(
    size   = 3.5,
    shape  = 21,
    color  = "black",
    stroke = 0.25
  ))
  
  text_theme <- theme(
    axis.title  = element_text(size = 10),
    legend.text = element_text(size = 8),
    axis.text   = element_text(size = 8)
  )
  
  # Reference UMAP
  if (!is.null(on_top)) {
    on_top <- ref_cols[on_top]
    
    ref_cols <- ref_cols[!names(ref_cols) %in% names(on_top)]
    ref_cols <- c(ref_cols, on_top)
  }
  
  ref_umap <- sobj_in %>%
    create_ref_umap(
      feature     = "subtype",
      color_guide = legd_guide,
      plot_cols   = ref_cols,
      pt_mtplyr   = pt_size / 0.1,
      pt_outline  = pt_outline,
      feat_levels = names(ref_cols)
    ) +
    theme(
      plot.margin     = unit(c(0.2, 1.5, 0.2, 0.2), "cm"),
      legend.position = "left",
      legend.margin   = margin(0.2, 0.2, 0.2, 1.5, "cm"),
      legend.text     = element_text(size = 8)
    )
  
  # Create list of feature UMAPs
  feat_umaps <- sobj_in %>%
    create_marker_umaps(
      pt_mtplyr       = pt_size / 0.1,
      add_outline     = pt_outline,
      input_markers   = feats,
      low_col         = low_col,
      high_col_mtplyr = high_col_mtplyr
    ) %>%
    map(~ {
      .x +
        guides(color = guide_colorbar(frame.colour = "black", frame.linewidth = 0.2)) +
        theme(plot.title = element_text(size = 12))
    })
  
  # Top panel of feature UMAPs
  top_umaps <- append(list(ref_umap), feat_umaps[1:2]) %>%
    plot_grid(
      plotlist   = .,
      rel_widths = c(1, 0.5, 0.5),
      nrow       = 1
    )
  
  # Bottom panel of feature UMAPs
  bot_umaps <- feat_umaps[3:6] %>%
    plot_grid(
      plotlist = .,
      nrow     = 1,
      align    = "h",
      axis     = "tb"
    )
  
  # Final feature UMAP figure
  res <- plot_grid(
    top_umaps, bot_umaps,
    ncol  = 1,
    align = "vh",
    axis  = "trbl"
  ) + 
    theme(plot.margin = unit(c(1, 0.2, 1.5, 0.2), "cm"))
  
  res
}

# Create figure 4 panels
create_fig4 <- function(sobj_in, feat_cols, ref_cols, ova_cols, pt_size = 0.00001, pt_outline = 0.4,
                        median_pt = 1, low_col = c("white", "white"), on_top = NULL,  gmm_column = "GMM_grp",
                        gmm_grps = c("ova low", "ova high")) {
  
  # Theme elements
  feats <- names(feat_cols)
  
  legd_guide <- guide_legend(override.aes = list(
    size   = 3.5,
    shape  = 21,
    color  = "black",
    stroke = 0.25
  ))
  
  text_theme <- theme(
    axis.title  = element_text(size = 10),
    legend.text = element_text(size = 8),
    axis.text   = element_text(size = 8)
  )
  
  # Set GMM groups in Seurat object
  sobj_in@meta.data <- sobj_in@meta.data %>%
    rownames_to_column("cell_id") %>%
    mutate(!!sym(gmm_column) := ifelse(
      !(!!sym(gmm_column)) %in% gmm_grps,
      "Other",
      !!sym(gmm_column)
    )) %>%
    column_to_rownames("cell_id")
  
  # GMM summary plots
  gmm_panels <- create_gmm_panels(
    sobj_in    = sobj_in,
    gmm_column = gmm_column,
    ova_cols   = ova_cols,
    bar_cols   = ref_cols,
    pt_size    = pt_size,
    pt_outline = pt_outline,
    show_bars  = T,
    plot_labs  = c(letters[1:3], "")
  )
  
  # Feature UMAPs
  feat_umaps <- create_feat_umap_panels(
    sobj_in    = sobj_in,
    ref_cols   = ref_cols,
    feats      = feat_cols,
    pt_size    = pt_size,
    pt_outline = pt_outline,
    low_col    = low_col,
    on_top     = on_top
  )
  
  # Feature boxplots
  box_data <- sobj_in %>%
    FetchData(c(feats, "subtype", gmm_column)) %>%
    as_tibble(rownames = "cell_id") %>%
    pivot_longer(cols = c(-cell_id, -subtype, -!!sym(gmm_column))) %>%
    mutate(type_name = str_c(subtype, "_", name)) %>%
    group_by(type_name) %>%
    mutate(
      up_qt = boxplot.stats(value)$stats[4],
      med   = median(value)
    ) %>%
    ungroup() %>%
    arrange(desc(med), desc(up_qt)) %>%
    mutate(
      name = fct_relevel(name, feats),
      type_name = fct_inorder(type_name)
    )
    
  feat_boxes <- box_data %>%
    ggplot(aes(type_name, value, fill = subtype)) +
    facet_wrap(~ name, nrow = 1, scales = "free_x") +
    scale_fill_manual(values = ref_cols) +
    scale_color_manual(values = ref_cols) +
    labs(y = "Counts") +
    theme_minimal_hgrid() +
    text_theme +
    theme(
      strip.text         = element_text(size = 12),
      legend.title       = element_blank(),
      legend.key.height  = unit(0.35, "cm"),
      axis.title.x       = element_blank(),
      axis.text.x        = element_blank(),
      axis.line.x        = element_blank(),
      axis.ticks.x       = element_blank(),
      axis.line.y        = element_line(size = 0.5, color = "grey85"),
      panel.grid.major.y = element_blank(),
      panel.background   = element_rect(fill = "#fafafa")
    )
  
  feat_boxes <- feat_boxes +
    stat_summary(geom = "point", shape = 22, fun = median, size = 0) +
    stat_summary(geom = "point", shape = 22, fun = median, size = median_pt + 1, color = "black") +
    geom_boxplot(
      size           = 0.3,
      width          = 0.6,
      fatten         = 0,
      outlier.colour = "grey85",
      outlier.alpha  = 1,
      outlier.size   = 0.1,
      show.legend    = F,
      coef           = 0,
    ) +
    stat_summary(
      aes(color = subtype),
      geom        = "point",
      shape       = 22,
      fun         = median,
      size        = median_pt,
      stroke      = 1,
      fill        = "white",
      show.legend = F
    ) +
    guides(fill = guide_legend(override.aes = list(size = 3.5, stroke = 0.25)))
  
  # Final bottom panel
  blank_gg <- ggplot() +
    theme_void()
  
  bot <- plot_grid(
    feat_boxes, blank_gg,
    rel_widths = c(1, 0.45)
  )
  
  # Create final figure
  res <- plot_grid(
    gmm_panels, feat_umaps, feat_boxes,
    rel_heights    = c(0.55, 1.05, 0.35),
    ncol           = 1,
    labels         = c("", "d", "e"),
    label_fontface = "plain",
    label_size     = 18
  )
  
  res
}

# Create figure S10 panels
create_figS10 <- function(sobj_in, feat_cols, ref_cols, ova_cols, pt_size = 0.00001, pt_outline = 0.4,
                          low_col = c("white", "white"), high_col_mtplyr = 1, on_top = NULL,  gmm_column = "GMM_grp",
                          gmm_grps = c("ova low", "ova high"), plot_labs) {
  
  # Set GMM groups in Seurat object
  sobj_in@meta.data <- sobj_in@meta.data %>%
    rownames_to_column("cell_id") %>%
    mutate(!!sym(gmm_column) := ifelse(
      !(!!sym(gmm_column)) %in% gmm_grps,
      "Other",
      !!sym(gmm_column)
    )) %>%
    column_to_rownames("cell_id")
  
  # GMM summary plots
  gmm_panels <- create_gmm_panels(
    sobj_in    = sobj_in,
    gmm_column = gmm_column,
    ova_cols   = ova_cols,
    bar_cols   = ref_cols,
    pt_size    = pt_size,
    pt_outline = pt_outline,
    show_bars  = F,
    plot_labs  = c(plot_labs[1:2], "", "")
  )
  
  # Feature UMAPs
  feat_umaps <- create_feat_umap_panels(
    sobj_in    = sobj_in,
    ref_cols   = ref_cols,
    feats      = feat_cols,
    pt_size    = pt_size,
    pt_outline = pt_outline,
    on_top     = on_top,
    low_col    = low_col,
    high_col_mtplyr = high_col_mtplyr
  )
  
  res <- plot_grid(
    gmm_panels, feat_umaps,
    rel_heights    = c(0.55, 1.05),
    ncol           = 1,
    labels         = c("", plot_labs[3:4]),
    label_fontface = "plain",
    label_size     = 18
  )
  
  res
}

# Create violin plots for DNA-tag counts
create_count_violins <- function(sobj_in, plot_cols, box_counts, type_column = "subtype",
                                 plot_title = NULL, control_types = c("B cell", "T cell")) {
  
  # Violin plot helper
  create_violins <- function(df_in, filt = NULL, color_id = type_column, plot_cols,
                             gg_title = NULL, plot_levels, as_swarm = F) {
    
    if (!is.null(filt)) {
      df_in <- df_in %>%
        filter(name == filt)
    }
    
    res <- df_in %>%
      mutate(!!sym(color_id) := fct_relevel(!!sym(color_id), plot_levels)) %>%
      ggplot(aes(counts + 1, !!sym(color_id))) +
      facet_wrap(~ name) +
      theme_minimal_vgrid() +
      theme(
        legend.position    = "none",
        plot.margin        = unit(c(0.2, 0.2, 1, 0.2), "cm"),
        plot.title         = element_text(size = 12, face = "plain"),
        strip.text         = element_text(size = 10),
        axis.title.y       = element_blank(),
        axis.title         = element_text(size = 10),
        axis.text          = element_text(size = 8),
        axis.ticks.x       = element_line(size = 0.1),
        panel.grid.major.x = element_line(size = 0.1)
      )
    
    if (as_swarm) {
      res <- res +
        geom_quasirandom(aes(color = !!sym(color_id)), size = 0.5, groupOnX = F) +
        scale_color_manual(values = plot_cols)
      
    } else {
      res <- res +      
        geom_violin(aes(fill = !!sym(color_id)), size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
        stat_summary(geom = "point", color = "black", fun = median) +
        scale_fill_manual(values = plot_cols)
    }
    
    if (!is.null(gg_title)) {
      res <- res +
        ggtitle(gg_title)
      
    }
    
    res
  }
  
  # Data for violin and beeswarm plots
  box_data <- sobj_in %>%
    FetchData(slot = "counts", vars = c(type_column, box_counts)) %>%
    as_tibble(rownames = "cell_id") %>%
    rename(all_of(box_counts)) %>%
    pivot_longer(cols = c(-cell_id, -!!sym(type_column)), values_to = "counts")
  
  # Plot levels
  box_levels <- box_data %>%
    filter(name == names(box_counts[1])) %>%
    mutate(!!sym(type_column) := fct_reorder(!!sym(type_column), counts, median)) %>%
    pull(type_column) %>%
    levels()
  
  box_levels <- box_levels[!box_levels %in% control_types] %>%
    c(control_types, .)
  
  # Create violin plots
  plot_args <- list(
    filt       = names(box_counts),
    as_swarm   = c(F, T, T),
    gg_title   = list(plot_title, NULL, NULL)
  )
  
  vlns <- plot_args %>%
    pmap(
      create_violins,
      df_in       = box_data,
      plot_cols   = plot_cols,
      plot_levels = box_levels
    )
  
  # Set equal x-axis scales
  vlns <- vlns %>%
    equalize_x(log_tran = T)
  
  # Create final figure
  res <- plot_grid(
    plotlist = vlns,
    nrow       = 1,
    align      = "vh",
    axis       = "trbl"
  )
  
  res
}

# Create correlation heatmaps for cell types
create_ref_heatmap <- function(sobj_in, ref_in, type_column = "subtype", plot_cols = NULL, rename_ref = NULL,
                               exclude_ref = "^Endothelial cells ", plot_title = NULL, return_mat = F) {
  
  # Get clustifyr matrix
  cor_mat <- sobj_in %>%
    clustify(
      cluster_col = type_column,
      ref_mat     = ref_in,
      seurat_out  = F
    )
  
  if (return_mat) {
    return(cor_mat)
  }
  
  # Heatmaps
  cor_df <- cor_mat %>%
    as_tibble(rownames = "Cell type") %>%
    rename(all_of(rename_ref)) %>%
    pivot_longer(cols = -`Cell type`, names_to = "Reference type", values_to = "r") %>%
    mutate(
      `Reference type` = fct_reorder(`Reference type`, r, mean, .desc = T),
      `Cell type` = fct_reorder(`Cell type`, r, mean)
    )
  
  # Exclude select cell types from reference
  if (!is.null(exclude_ref)) {
    cor_df <- cor_df %>%
      filter(!grepl(exclude_ref, `Reference type`))
  }
  
  # Create heatmap
  res <- cor_df %>%
    ggplot(aes(`Reference type`, `Cell type`, fill = r)) +
    geom_tile(color = "white", size = 1) +
    scale_fill_gradient(low = "white", high = plot_cols) +
    guides(fill = guide_colorbar(barwidth = unit(0.2, "cm"), frame.colour = "black", frame.linewidth = 0.1)) +
    theme_info +
    theme(
      plot.title   = element_text(size = 12, face = "plain"),
      strip.text   = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text  = element_text(size = 8),
      axis.title   = element_text(size = 10),
      axis.text.x  = element_text(angle = 45, hjust = 1),
      axis.text    = element_text(size = 8),
      axis.ticks   = element_blank(),
      axis.line    = element_blank()
    )
  
  
  if (!is.null(plot_title)) {
    res <- res +
     ggtitle(plot_title)
  }
  
  res
}

# Plot correlation
plot_corr <- function(sobj_in, x, y, feat, data_slot, cols_in, plot_title,
                      add_y_pseudo = 1, ...) {
  
  res <- sobj_in %>%
    FetchData(c(x, y, feat), slot = data_slot) %>%
    mutate(
      !!sym(x) := log10(!!sym(x)),
      !!sym(y) := log10(!!sym(y) + add_y_pseudo)
    ) %>%
    plot_features(
      x         = x,
      y         = y,
      feature   = feat,
      data_slot = "counts",
      plot_cols = cols_in,
      # lab_pos   = c(0.35, 1),
      lab_pos   = "strip",
      lab_size  = 5,
      calc_cor  = T,
      lm_line   = T,
      ...
    ) +
    ggtitle(plot_title) +
    guides(color = guide_legend(override.aes = list(size = 3.5))) +
    theme_info +
    theme(legend.title = element_blank())
  
  res
}

# Calculate pairwise p-values for gg objects
calc_p_vals <- function(gg_in, sample_name, data_column, type_column, log_tran = T) {
  
  # Pull data from gg object
  gg_data <- gg_in$data
  
  # Log transform
  if (log_tran) {
    gg_data <- gg_data %>%
      mutate(!!sym(data_column) := log10(!!sym(data_column)))
  }
  
  # Calculate median
  gg_stats <- gg_data %>%
    group_by(!!sym(type_column)) %>%
    summarize(med = median(!!sym(data_column)))
  
  # Run wilcox test
  gg_counts <- gg_data %>%
    pull(data_column)
  
  gg_groups <- gg_data %>%
    pull(type_column)
  
  res <- gg_counts %>%
    pairwise.wilcox.test(
      g = gg_groups, 
      p.adj = "bonf"
    ) %>%
    tidy()
  
  # Add medians to data.frame
  res <- gg_stats %>%
    rename(med_1 = med) %>%
    right_join(res, by = c("cell_type" = "group1"))
  
  res <- gg_stats %>%
    rename(med_2 = med) %>%
    right_join(res, by = c("cell_type" = "group2"))
  
  # Format final table
  res <- res %>%
    mutate(Sample = sample_name) %>%
    select(
      Sample,
      `Cell type 1`             = str_c(type_column, ".y"),
      `Median OVA FC 1 (log10)` = med_1,
      `Cell type 2`             = type_column,
      `Median OVA FC 2 (log10)` = med_2,
      p.value
    )
  
  res
}

```

```{r "Setup", echo = F}

# Seurat objects used for subtype annotations
sobjs_sub <- read_rds(here(params$rds_dir, "sobjs_subsets.rds"))

# Order of UMAP layers
subtype_order <- list(
  d2_DC   = c("CCR7hi Mig cDC2", "CCR7hi Mig cDC1", "B cell", "T cell"),
  d14_DC  = c("CCR7hi Mig cDC2", "CCR7hi Mig cDC1", "cDC2 Tbet-", "cDC2 Tbet+", "B cell", "T cell", "NK"),
  d2_LEC  = NULL,
  d14_LEC = c("Ptx3_LEC", "fLEC", "cLEC", "Collecting", "BEC", "B cell", "T cell"),
  d2_FRC  = NULL,
  d14_FRC = NULL
)

# Parameter lists
fig3_names <- c("d2_DC", "d14_DC", "d14_LEC", "d14_FRC")
fig3_sobjs <- sobjs[fig3_names]

fig3_params <- list(
  sobj_in    = fig3_sobjs, 
  plot_title = so_titles[names(fig3_sobjs)],
  cols_in    = so_cols[names(fig3_sobjs)],
  on_top     = subtype_order[names(fig3_sobjs)]
)

corr_params <- list(
  sobj_in    = sobjs, 
  plot_title = so_titles[names(sobjs)], 
  cols_in    = so_cols[names(sobjs)]
)

```

# Figure 3

Cell types associated with high antigen counts. (a, d, g, j) UMAP projections are shown for DCs, LECs, and FRCs. (b, e, h, k) Relative ova signal was calculated by dividing antigen counts for each cell by the median antigen counts for T and B cells. (c, f, i, l) Antigen counts are displayed on UMAP projections for each cell type.

```{r "Fig 3", fig.width = 13, fig.height = 18}

# Create panel plots
gg_list <- fig3_params %>%
  pmap(
    create_fig3,
    box_counts   = c("Relative ova signal" = "ova_fc"), 
    umap_counts  = c("ova counts" = "adt_ovalbumin"),
    data_slot    = "counts",
    pt_size_2    = 0.1,
    pt_outline_2 = 0.4
  ) %>%
  flatten()

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create table of p-values
if (!is.null(params$p_val_xlsx)) {
  p_vals <- gg_list[violin_idx] %>%
    imap(
      calc_p_vals,
      data_column = "Relative ova signal",
      type_column = "cell_type",
      log_tran    = T
    ) %>%
    bind_rows()
  
  file_out <- here(params$p_val_xlsx)
  
  p_vals %>%
    write.xlsx(file_out)
  
  FILES_OUT <- c(FILES_OUT, md5sum(file_out))
}

# Create final figure
fig3 <- gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

fig3

```

\newpage

# Figure 4

Genes associated with high antigen counts for day 14 LECs. (a) LECs containing low and high antigen counts were identified using a gaussian mixture model. A UMAP projection is shown for ova-low and ova-high cells. T cells, B cells, and epithelial cells are shown in white (Other). (b) The distribution of ova antigen counts is shown for ova-low and ova-high cells. Dotted lines indicate the mean counts for each population. (c) The fraction of cells belonging to each LEC cell type is shown for ova-low and ova-high populations. (d) UMAP projections show the expression of top ova-high markers. (e) The expression of ova-high markers was plotted for each cell type.

```{r "Fig 4", fig.width = 10, fig.height = 11.5}

# Genes of interest
genes <- c("Prox1", "Cavin1", "Cavin2", "Stab1", "Stab2", "Nfat5")

# Seurat object for figure
so_name <- "d14_LEC"

fig_4 <- create_fig4(
  sobj_in    = sobjs[[so_name]],
  feat_cols  = set_names(feat_cols, genes),
  ref_cols   = so_cols[[so_name]],
  ova_cols   = ova_cols,
  on_top     = subtype_order[[so_name]],
  gmm_column = "GMM_grp",
  gmm_grps   = c("ova low", "ova high")
)

fig_4

```

\newpage

# Figure S5

Comparison of ova-psDNA, psDNA, and pDNA signal for each cell type. Counts are shown for ova-psDNA, psDNA, and pDNA for DCs (a, b), LECs (c), and FRCs (d).  

```{r "Fig S5", fig.width = 11, fig.height = 15}

box_counts <- c(
  "ovalbumin" = "adt_ovalbumin",
  "psDNA"     = "adt_protected-DNA",
  "pDNA"      = "adt_unprotected-DNA"
)

fig_S5 <- sobjs[fig3_names] %>%
  imap(~ {
    create_count_violins(
      sobj_in     = .x,
      plot_cols   = so_cols[[.y]],
      box_counts  = box_counts,
      type_column = "subtype",
      plot_title  = so_titles[[.y]]
    )
  }) %>%
  plot_grid(
    plotlist       = .,
    ncol           = 1,
    labels         = letters,
    label_fontface = "plain",
    label_size     = 18,
    align          = "vh",
    axis           = "trbl"
  )

fig_S5


```

\newpage

# Figure S6

Antigen counts were compared with total mRNA counts for each cell for DCs (a, b), LECs (c, d), and FRCs (e, f).

```{r, fig.width = 20, fig.height = 34}

pad <- c(9.5, 2, 9.8, 2, 9.8, 2)

cor_plots <- corr_params %>%
  pmap(
    plot_corr,
    x         = c("RNA counts (log10)" = "nCount_RNA"),
    y         = c("ova counts + 1 (log10)" = "adt_ovalbumin"),
    feat      = "subtype",
    split_id  = "subtype",
    data_slot = "counts",
    pt_size   = 1,
    scales    = "free",
    ncol      = 3
  ) %>%
  map2(pad, ~ {
    .x + theme(
      legend.position = "none",
      strip.text      = element_text(size = 14),
      plot.margin     = unit(c(0.2, 0.2, .y, 0.2), "cm")
    )
  })

plot_grid(
  plotlist       = cor_plots,
  rel_heights    = c(1, 0.8, 0.8),
  labels         = letters,
  label_size     = 32,
  label_fontface = "plain",
  align          = "v",
  ncol           = 2
)

```

\newpage

# Figure S7

LEC cell types associated wih high antigen counts for the day 2 timepoint. (a) A UMAP projection is shown for LEC cell types, epithelial cells, B cells, and T cells identified for the day 2 timepoint. (b) Relative ova signal is shown for each cell type. Relative ova signal was calculated by dividing antigen counts for each cell by the median antigen counts for T and B cells. (c) Antigen counts are displayed on the UMAP projection shown in (a). (d, e) Correlation coefficients are shown comparing each identified LEC cell type with the reference cell types from Xiang et al. 

```{r, fig.width = 13, fig.height = 9}

# Create UMAPs and violin plots for d2_LEC
so_name <- "d2_LEC"

gg_list <- sobjs[[so_name]] %>%
  create_fig3(
    box_counts   = c("Relative ova signal" = "ova_fc"), 
    umap_counts  = c("ova counts" = "adt_ovalbumin"),
    data_slot    = "counts",
    cols_in      = so_cols[[so_name]],
    plot_title   = so_titles[[so_name]],
    on_top       = subtype_order[[so_name]],
    pt_size      = 0.5,
    pt_outline   = 0.8,
    pt_size_2    = 0.5,
    pt_outline_2 = 0.8
  )

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create correlation heatmaps for LEC annotations
LEC_names <- c("d2_LEC", "d14_LEC")
heat_cols <- c(get_cols()[2], get_cols()[3])

heat_maps <- map2(LEC_names, heat_cols, ~ {
  create_ref_heatmap(
    sobj_in    = sobjs_sub[[.x]],
    ref_in     = subtype_refs[[so_types[.x]]],
    plot_cols  = .y,
    plot_title = so_titles[[.x]],
    rename_ref = c("BEC (ImmGen)" = "BEC")
  )
})

# Create final figure
fig_S7 <- (gg_list[[1]] | gg_list[[2]] | gg_list[[3]]) /
  (heat_maps[[1]] | heat_maps[[2]]) +
  plot_layout(heights = c(1, 0.6)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(0, 1)
  )

fig_S7

```

\newpage

# Figure S9

FRC cell types associated wih high antigen counts for the day 2 timepoint. (a) A UMAP projection is shown for FRC cell types, B cells, and T cells identified for the day 2 timepoint. (b) Relative ova signal is shown for each cell type. Relative ova signal was calculated by dividing antigen counts for each cell by the median antigen counts for T and B cells. (c) Antigen counts are displayed on the UMAP projection shown in (a).

```{r, fig.width = 13, fig.height = 5}

# Create UMAPs and violine plots for d2_FRC
so_name <- "d2_FRC"

gg_list <- sobjs[[so_name]] %>%
  create_fig3(
    box_counts   = c("Relative ova signal" = "ova_fc"), 
    umap_counts  = c("ova counts" = "adt_ovalbumin"),
    data_slot    = "counts",
    cols_in      = so_cols[[so_name]],
    plot_title   = so_titles[[so_name]],
    on_top       = subtype_order[[so_name]],
    pt_size      = 1.5,
    pt_outline   = 2,
    pt_size_2    = 1.5,
    pt_outline_2 = 2
  )

# Set violin scales equal
violin_idx <- seq_along(gg_list) %% 3 == 2
gg_list[violin_idx] <- gg_list[violin_idx] %>%
  equalize_x(log_tran = T)

# Create final figure
fig_S9 <- gg_list %>%
  wrap_plots(ncol = 3, widths = c(1, 0.75, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    plot.margin = unit(c(1, 0.5, 0.5, 0.5), "cm"),
    plot.tag = element_text(size = 24, face = "plain"),
    plot.tag.position = c(-0.08, 1)
  )

fig_S9

```

\newpage

# Figure S10

Genes associated with high antigen counts for day 2 and day 14 cDC2 Tbet- cells. (a, d) Day 2 (a) and day 14 (d) cDC2 Tbet- cells containing low and high antigen counts were identified using a gaussian mixture model. A UMAP projection is shown for ova-low and ova-high cells. Cell types not included in the comparison are shown in white (Other). (b, e) The distribution of ova antigen counts is shown for ova-low and ova-high cDC2 Tbet- cells. Dotted lines indicate the mean counts for each population. (c, f) UMAP projections show the expression of top markers associated with ova-high cDC2 Tbet- cells.

```{r, fig.width = 10, fig.height = 18}

# Seurat objects, genes, cell types
so_names <- c("d2_DC", "d14_DC")
type <- "cDC2 Tbet-"

genes <- list(
  "d2_DC"  = c("Ccl2", "Cxcl2", "Mif", "Msr1", "Pkm", "Lgals3"),
  "d14_DC" = c("Fcgr4", "Cd72", "Prkcb", "Acp5", "Itgam", "Pecam1")
) %>%
  map(set_names, x = feat_cols)

# OVA colors and groups
fig_cols <- rev(ova_cols)

names(fig_cols) <- names(fig_cols) %>%
  str_c(if_else(. != "Other", str_c(type, "-"), ""), .)
  
gmm_grps <- names(fig_cols)[names(fig_cols) != "Other"]

# Figure parameters
plot_args <- list(
  sobj_in   = sobjs[so_names],
  feat_cols = genes[so_names],
  ref_cols  = so_cols[so_names],
  on_top    = subtype_order[so_names],
  plot_labs = list(letters[1:3], letters[4:6]),
  low_col   = list(c("white", "white"), "white"),
  high_col_mtplyr = list(c(1, 2, rep(1, 4)), 1)
)

# Create figures
fig_S10 <- plot_args %>%
  pmap(
    create_figS10,
    ova_cols   = fig_cols,
    gmm_column = "type_GMM_grp_2",
    gmm_grps   = gmm_grps
  ) %>%
  plot_grid(
    plotlist = .,
    ncol     = 1,
    align    = "vh", 
    axis     = "trbl"
  )

fig_S10

```




