---
title: "Antigen Tracking Analysis"
author: "Ryan Sheridan"
date: "`r Sys.Date()`"

output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    df_print: "paged"
    code_folding: "hide"
    self_contained: true
    highlight: "kate"
    
params:
  genome:        "mmusculus"                        # Genome to use for GO analysis
  template_dir:  "src"                              # Directory containing template Rmarkdowns
  rds_dir:       "sobjs/so"                         # Direcotry to use for loading/saving Seurat objects
  ref_dir:       "ref"                              # Directory to use for loading/saving clustifyr references
  xlsx_dir:      "results/gex_analysis/gene_lists"  # Directory to use for writing gene lists (comment out to skip)
  p_max_markers: 0.05                               # Max p-value for marker genes
  FC_min:        0.25                               # Min fold change for marker genes
  auc_min:       0.5                                # Min AUC for marker genes
  pct_in_min:    50                                 # Min percentage cells expressing marker in group 
  pct_out_max:   100                                # Max percentage cells expressing marker outside group
  uniq_markers:  FALSE                              # Remove markers that are present in more than one group
  p_max_GO:      0.05                               # Max p-value for GO terms
  term_size:     15                                 # Min size of GO term
  intrsct_size:  3                                  # Min intersection with GO term
  order_query:   TRUE                               # Markers are ordered by fold change and submitted as an ordered query
  uniq_GO:       TRUE                               # Remove GO terms that are present in more than one group
  
  # These parameters specify the input matrices and cell types that should be used for analysis
  # mat_in: Cellranger output folder.
  # cell_type: Cell type used for subsetting Seurat objects.
  # title: Section title.
  # sobj_out: The output Seurat object that is saved after processing and subsetting based on cell type.
  sobjs:
    value:
      d2_DC:
        mat_in:    "results/GEX_CD45pos_d2-ADT_CD45pos_d2/outs/filtered_feature_bc_matrix"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 2)"
        sobj_out:  "d2_DC_so_2.rds"
      d14_DC:
        mat_in:    "results/GEX_CD45pos_d14-ADT_CD45pos_d14/outs/filtered_feature_bc_matrix"
        cell_type: "DC"
        title:     "Myeloid Cells (Day 14)"
        sobj_out:  "d14_DC_so_2.rds"
      d2_LEC:
        mat_in:    "results/GEX_CD45neg_d2-ADT_CD45neg_d2/outs/filtered_feature_bc_matrix"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 2)"
        sobj_out:  "d2_LEC_so_2.rds"
      d14_LEC:
        mat_in:    "results/GEX_CD45neg_d14-ADT_CD45neg_d14/outs/filtered_feature_bc_matrix"
        cell_type: "LEC"
        title:     "Endothelial/Stromal Cells (Day 14)"
        sobj_out:  "d14_LEC_so_2.rds"
      d2_FRC:
        mat_in:    "results/GEX_CD45neg_d2-ADT_CD45neg_d2/outs/filtered_feature_bc_matrix"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 2)"
        sobj_out:  "d2_FRC_so_2.rds"
      d14_FRC:
        mat_in:    "results/GEX_CD45neg_d14-ADT_CD45neg_d14/outs/filtered_feature_bc_matrix"
        cell_type: "fibroblast"
        title:     "Fibroblast/Stromal Cells (Day 14)"
        sobj_out:  "d14_FRC_so_2.rds"
  
  # These parameters specify paths to clustifyr references
  ref_sobjs: ["d2_so.rds", "d14_so.rds"]
  type_ref:  "ref_celltype_walsh.rda"
  xiang_ref: "ref_LEC_xiang.rda"
  subtype_refs:
    value:
      DC:         "ref_DC_walsh.rda"
      LEC:        "ref_LEC_walsh.rda"
      fibroblast: "ref_FRC_walsh.rda"
---

<br>

#### Parameters

* Markers p-value cutoff: **`r params$p_max_markers`**
* Minimum marker gene log fold change: **`r params$FC_min`**
* Minimum marker gene AUC: **`r params$auc_min`**
* Minimum percentage of cells expressing marker in group: **`r params$pct_in_min`%**
* Maximum percentage of cells expressing marker outside group: **`r params$pct_out_max`%**
* Remove markers present in more than one group: **`r params$uniq_markers`**

* Genome for GO query: **`r params$genome`**
* GO terms p-value cutoff: **`r params$p_max_GO`**
* Minimum size of GO term: **`r params$term_size`**
* Minimum intersection with GO term: **`r params$intrsct_size`**
* Order markers by fold change and submit as an ordered GO query: **`r params$order_query`**
* Remove GO terms present in more than one group: **`r params$uniq_GO`**

---

<br>

`r knitr::knit_child(here::here(params$template_dir, "setup.Rmd"))`

```{r "Run markers chunks", echo = F}

# Create list of chunks
template <- here(params$template_dir, "markers_template.Rmd")

chunks <- names(sobjs) %>%
  map(~ knit_expand(template))

```

`r knit_child(text = chunks)`

## Input files

```{r "Input meta data"}

FILES_IN %>%
  tibble(
    path = names(.),
    checksum = .
  ) %>%
  arrange(path)

```

---

<br>

<br>

## Output files

```{r "Output meta data"}

FILES_OUT %>%
  tibble(
    path = names(.),
    checksum = .
  ) %>%
  arrange(path)

```

---

<br>

<br>

## Session info

```{r, comment = "", echo = F}
session_info()
```


