
```{r "{{.x}} Setup", echo = F}

comparison <- c("{{.x[1]}}", "{{.x[2]}}")

if ({{.y}} > 2) {
  comparison[{{.y}}] <- c("{{.x[3]}}")
}

if ({{.y}} > 3) {
  stop("Comparisons cannot include more than three groups.")
}

rds_files <- str_c(comparison, "_so.rds") %>%
  file.path(params$rds_dir, .)

names(rds_files) <- comparison

sect_title <- comparison %>%
  reduce(str_c, sep = " ")

```

## **`r sect_title`**

### Sample Markers

UMAPs showing the sample identity or ovalbumin signal is included on the left, ovalbumin signal for each sample is shown on the right
```{r "{{.x}} Sample OVA summary", fig.width = 8.5, fig.height = 4}

# Load Seurat objects
sobjs <- rds_files %>%
  map(read_rds)

# Add orig.ident and cell_type to meta.data
sobjs <- sobjs %>%
  imap(AddMetaData, "orig.ident") %>%
  imap(~ {
    col_id <- .y %>%
      str_extract("[A-Z]+$") %>%
      str_c("cell_type", .)
    
    res <- .x %>%
      FetchData(col_id) %>%
      AddMetaData(
        object   = .x,
        metadata = .,
        col.name = "cell_type"
      )
    
    if ("ova" %in% rownames(res@assays$adt)) {
      res <- res %>%
        FetchData("adt_ova") %>%
        AddMetaData(
          object = res,
          metadata = .,
          col.name = "adt_ovalbumin"
        )
    }
    
    res
  })

# Merge objects and run PCA, UMAP, clustering
sobj <- sobjs %>%
  merge_sobj(sample_order = names(sobjs)) %>%
  cluster_RNA(resolution = 0.6) %>%
  AddMetaData(
    metadata = Embeddings(., reduction = "umap"),
    col.name = c("UMAP_1", "UMAP_2")
  )

# Set sample order and colors
sample_cols <- theme_cols[1:length(sobjs)]
names(sample_cols) <- names(sobjs)

# Add cell type cluster column
sobj@meta.data <- sobj@meta.data %>%
  rownames_to_column("cell_id") %>%
  mutate(
    orig.ident = fct_relevel(orig.ident, names(sample_cols)),
    sample_types = str_c(orig.ident, "-", cell_type)
  ) %>%
  column_to_rownames("cell_id")

# Sample UMAP
sample_umap <- sobj %>%
  plot_features(
    feature    = "orig.ident",
    pt_size    = 0.1,
    pt_outline = 0.4,
    plot_cols  = sample_cols
  ) +
  guides(color = guide_legend(override.aes = list(size = 3.5, shape = 21, color = "black", stroke = 0.25))) +
  scale_fill_manual(values = sample_cols) +
  blank_theme +
  theme(
    legend.position = "top",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 10)
  )

# OVA UMAP
ova_umap <- sobj %>%
  plot_features(
    feature    = "adt_ovalbumin",
    pt_size    = 0.1,
    pt_outline = 0.2,
    plot_cols  = c("#fafafa", sample_cols[2])
  ) +
  ggtitle("adt_ovalbumin") +
  blank_theme +
  theme(
    plot.title        = element_text(size = 13),
    legend.position   = "bottom",
    legend.title      = element_blank(),
    legend.text       = element_text(size = 8),
    legend.key.height = unit(0.1, "cm"),
    legend.key.width  = unit(0.3, "cm")
  )

# Plot OVA counts
ova_boxes <- sobj %>%
  FetchData(c("orig.ident", "adt_ovalbumin")) %>%
  as_tibble(rownames = "cell_id") %>%
  ggplot(aes(orig.ident, adt_ovalbumin + 0.01, color = orig.ident)) +
  geom_quasirandom(size = 1, color = "black") +
  geom_quasirandom(size = 0.5) +
  stat_summary(fun = "median", geom = "point", shape = 21, size = 2, show.legend = F, fill = "white", color = "black", stroke = 0.5) +
  scale_color_manual(values = sample_cols) +
  scale_y_log10() +
  guides(color = col_guide) +
  theme_info +
  theme(
    legend.position = "none",
    axis.title.x    = element_blank(),
    axis.title.y    = element_text(size = 13),
    axis.text.y     = element_text(size = 8),
    axis.text.x     = element_blank(),
    axis.ticks.x    = element_blank(),
    axis.line.x     = element_blank()
  )

# Create final figure
plot_grid(
  sample_umap, ova_umap, ova_boxes,
  rel_widths = c(0.62, 0.62, 0.38),
  nrow = 1,
  align = "h",
  axis = "trbl"
)

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing cells from each sample. Gene expression signal is shown for the top marker genes for each sample (top, middle). GO terms were identified for marker genes, the top terms are labeled (bottom).
```{r "{{.x}} Sample markers", fig.width = 8.5, fig.height = 14, results = "asis"}

# Create figures
fig_umap <- sample_umap +
  theme(legend.text = element_text(size = 10))

create_marker_panel_v1(
  input_sobj   = sobj,
  input_cols   = sample_cols,
  input_umap   = fig_umap,
  clust_column = "orig.ident",
  n_boxes      = 18,
  all_boxes    = T
)

```

### Cell Type Markers

UMAPs colored based on cell type or ovalbumin signal are shown below. Ovalbumin signal for each cell type is shown on the left and the composition of each sample is shown on the right.
```{r "{{.x}} Cell type OVA summary", fig.width = 8.5, fig.height = 7.3}

# Set cell type order and colors
cell_types <- sobj@meta.data %>%
  pull(cell_type) %>%
  unique()

names(cell_types) <- cell_types

type_cols <- theme_cols
names(type_cols) <- cell_types
type_cols <- type_cols[!is.na(names(type_cols))]

sam_type_cols <- type_cols %>%
  imap(~ {
    colors <- c("#000000", .x, "#8C82A3")
    
    for (i in seq_along(comparison)) {
      names(colors)[i] <- str_c(comparison[i], "-", .y)
    }
    
    colors <- colors[!is.na(names(colors))]
  }) %>%
  reduce(c)

# Cell type UMAP
type_umap <- sobj %>%
  plot_features(
    feature    = "cell_type",
    pt_size    = 0.1,
    pt_outline = 0.4,
    plot_cols  = type_cols
  ) +
  guides(color = guide_legend(override.aes = list(size = 3.5, shape = 21, color = "black", stroke = 0.25))) +
  scale_fill_manual(values = type_cols) +
  blank_theme +
  theme(
    legend.position = "right",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 8)
  )

# OVA UMAP
ova_umap <- sobj %>%
  plot_features(
    feature    = "adt_ovalbumin",
    pt_size    = 0.1,
    pt_outline = 0.2,
    plot_cols  = c("#fafafa", type_cols[4])
  ) +
  ggtitle("adt_ovalbumin") +
  blank_theme +
  theme(
    plot.title        = element_text(size = 13),
    legend.position   = "bottom",
    legend.key.height = unit(0.1, "cm"),
    legend.key.width  = unit(0.3, "cm"),
    legend.title      = element_blank(),
    legend.text       = element_text(size = 8)
  )

# OVA boxplots
ova_data <- sobj %>%
  FetchData(c("adt_ovalbumin", "orig.ident", "cell_type")) %>%
  as_tibble(rownames = "cell_id") %>%
  mutate(cell_type  = fct_reorder(cell_type, adt_ovalbumin, median, .desc = T))

ova_boxes <- ova_data %>%
  ggplot(aes(orig.ident, adt_ovalbumin + 0.01, color = cell_type)) +
  geom_quasirandom(size = 0.5, color = "black") +
  geom_quasirandom(size = 0.25) +
  facet_wrap(~ cell_type, nrow = 1) +
  scale_color_manual(values = type_cols) +
  guides(color = col_guide) +
  scale_y_log10() +
  theme_info +
  theme(
    strip.background = element_blank(),
    strip.text       = element_blank(),
    legend.position  = "none",
    legend.title     = element_blank(),
    axis.title.x     = element_blank(),
    axis.title.y     = element_text(size = 13),
    axis.text        = element_text(size = 8),
    axis.text.x      = element_text(angle = 90, vjust = 0.5, hjust = 1)
  )

# Create OVA bar graphs
ova_bars <- sobj %>%  
  plot_cell_count(
    group_id    = "orig.ident",
    split_id    = NULL,
    fill_id     = "cell_type",
    plot_colors = type_cols,
    bar_line    = 0.2
  ) +
  theme_info +
  theme(
    legend.title = element_blank(),
    legend.text  = element_text(size = 8),
    axis.text    = element_text(size = 8),
    axis.text.x  = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 13)
  )

# Create final figure
umaps <- plot_grid(
  type_umap, ova_umap,
  rel_widths = c(0.55, 0.35),
  nrow  = 1,
  align = "h",
  axis  = "trbl"
)

boxes <- plot_grid(
  ova_boxes, ova_bars,
  rel_widths = c(0.63, 0.37),
  align = "h",
  axis  = "trbl"
)

plot_grid(
  umaps, boxes,
  rel_heights = c(0.55, 0.45),
  nrow = 2,
  align = "v",
  axis  = "l"
)

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by splitting the cells based on cell type and comparing each sample. Gene expression signal is shown for the top marker genes for each cell type cluster (top, middle). GO terms were identified for marker genes, the top terms are labeled (bottom).
```{r "{{.x}} Cell type markers", fig.width = 8.5, fig.height = 14, results = "asis"}

# Find cell type markers
fig_markers <- cell_types %>%
  map(~ {
    find_group_markers(
      input_grp  = .x,
      input_sobj = sobj,
      grp_col    = "cell_type",
      clust_col  = "sample_types"
    )
  }) %>%
  compact() %>%
  bind_rows()

# Create figures
create_marker_panel_v2(
  input_sobj    = sobj,
  input_markers = fig_markers,
  input_cols    = sam_type_cols,
  grp_column    = "cell_type",
  clust_column  = "sample_types", 
  color_guide   = outline_guide,
  n_boxes       = 18,
  all_boxes     = T
)

```

### Ovalbumin Markers

Cells were divided into groups based on ovalbumin signal. A UMAP projection showing the ovalbumin groups included on the left and the fraction of cells belonging to each group is shown on the right. 
```{r "{{.x}} OVA cluster summary", fig.width = 7, fig.height = 4.3}

# Determine number of OVA groups
n_grps <- floor(ncol(sobj) / 100)

if (n_grps > 6) {
  n_grps <- 6
}

if (n_grps < 2) {
  n_grps <- 2
}

# Set OVA colors
ova_cols <- c(
  "#e31a1c",  # red
  "#fec44f",  # yellow
  "#6a51a3",  # purple
  "#225ea8",  # blue
  "#ec7014",  # orange
  "#238443"   # green
)

names(ova_cols) <- as.character(1:n_grps)

# Divide cells based on OVA signal
sobj <- sobj %>%
  FetchData(c("orig.ident", "adt_ovalbumin")) %>%
  rownames_to_column("cell_id") %>%
  mutate(
    ova_group   = ntile(adt_ovalbumin, n_grps),
    ova_group   = as.character(ova_group),
    ova_group   = fct_relevel(ova_group, names(ova_cols)),
    ova_sam_grp = str_c(orig.ident, "-", ova_group)
  ) %>%
  column_to_rownames("cell_id") %>%
  AddMetaData(
    object = sobj,
    metadata = .
  )

# OVA groups UMAP
ova_umap <- sobj %>%
  plot_features(
    feature    = "ova_group",
    pt_size    = 0.1,
    pt_outline = 0.4,
    plot_cols  = ova_cols
  ) +
  guides(color = guide_legend(override.aes = list(size = 3.5, shape = 21, color = "black", stroke = 0.25), nrow = 1)) +
  scale_fill_manual(values = ova_cols) +
  ggtitle("Ovalbumin Group") +
  blank_theme +
  theme(
    plot.title       = element_text(size = 13),
    legend.position = "top",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 8)
  )

# OVA boxplots
ova_boxes <- sobj %>%
  FetchData(c("adt_ovalbumin", "orig.ident", "ova_group")) %>%
  as_tibble(rownames = "cell_id") %>%
  ggplot(aes(orig.ident, adt_ovalbumin + 0.01, color = ova_group)) +
  geom_quasirandom(size = 1, color = "black") +
  geom_quasirandom(size = 0.5) +
  scale_color_manual(values = ova_cols) +
  guides(color = col_guide) +
  scale_y_log10() +
  theme_info +
  theme(
    strip.background = element_blank(),
    strip.text       = element_blank(),
    legend.position  = "none",
    legend.title     = element_blank(),
    axis.title.x     = element_blank(),
    axis.title.y     = element_text(size = 13),
    axis.text        = element_text(size = 8),
    axis.text.x      = element_text(angle = 90, vjust = 0.5, hjust = 1)
  )

# OVA bar graphs
ova_bars <- sobj %>%
  plot_cell_count(
    group_id    = "orig.ident",
    split_id    = NULL,
    fill_id     = "ova_group",
    plot_colors = ova_cols,
    order_count = F,
    bar_line = 0.2
  ) +
  theme_info +
  theme(
    legend.position = "none",
    axis.text       = element_text(size = 8),
    axis.text.x     = element_text(angle = 90, vjust = 0.5, hjust = 1),
    axis.title.x    = element_blank(),
    axis.title.y    = element_text(size = 13)
  )

# Create final figure
plot_grid(
  ova_umap, ova_boxes, ova_bars,
  rel_widths = c(0.55, 0.3, 0.3),
  nrow       = 1,
  align      = "h",
  axis       = "trbl"
)

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing the samples for each ovalbumin group. Gene expression signal is shown for the top marker genes for each group (top, middle). GO terms were identified for marker genes, the top terms are labeled (bottom).
```{r "{{.x}} OVA cluster markers", fig.width = 8.5, fig.height = 14, results = "asis"}

# Find markers for each OVA group
fig_markers <- names(ova_cols) %>%
  map(~ {
    find_group_markers(
      input_grp  = .x,
      input_sobj = sobj,
      grp_col    = "ova_group",
      clust_col  = "ova_sam_grp"
    )
  }) %>%
  compact() %>%
  bind_rows()

# Figure colors and order
fig_colors <- ova_cols %>%
  imap(~ {
    colors <- c("#000000", .x)
    
    for (i in seq_along(comparison)) {
      names(colors)[i] <- str_c(comparison[i], "-", .y)
    }
    
    colors <- colors[!is.na(names(colors))]
  }) %>%
  reduce(c)

# Crate figures
create_marker_panel_v2(
  input_sobj    = sobj,
  input_markers = fig_markers,
  input_cols    = fig_colors,
  grp_column    = "ova_group",
  clust_column  = "ova_sam_grp", 
  color_guide   = outline_guide,
  n_boxes       = 18,
  all_boxes     = T
)

```



```{r "{{.x}} OVA CLUSTERS", fig.width = 8.5, fig.height = 13, results = "asis", eval = F, echo = F}

# OVA markers
Idents(sobj) <- sobj %>%
  FetchData("ova_group")

ova_markers <- sobj %>%
  FindAllMarkers(only.pos = T) %>%
  as_tibble() %>%
  filter(p_val_adj < 0.05)

# OVA cluster plots
for (i in seq_along(ova_cols)) {
  cat("\n#### ova_group-", names(ova_cols[i]), "\n", sep = "")
  
  umap_levels <- ova_cols[ova_cols != ova_cols[i]]
  umap_levels <- c(umap_levels, ova_cols[i]) %>%
    names()
  
  # OVA groups UMAP
  ova_umap <- sobj %>%
    plot_features(
      feature     = "ova_group",
      plot_cols   = ova_cols,
      feat_levels = umap_levels
    ) +
    guides(color = col_guide) +
    blank_theme +
    theme(
      legend.position = "top",
      legend.title    = element_blank(),
      legend.text     = element_text(size = 10)
    )

  # OVA figure
  ova_marks <- ova_markers %>%
    filter(cluster == names(ova_cols[i]))
  
  ova_marks_fig <- sobj %>%
    create_marker_fig(
      input_markers = ova_marks,
      type_id       = "ova_group",
      input_umap    = ova_umap,
      umap_color    = ova_cols[[i]],
      box_colors    = ova_cols
    )

  print(ova_marks_fig)
  cat("\n\n---\n\n<br>\n\n<br>\n\n")
}
  
```

```{r "{{.x}} INTEGRATE DATA", fig.width = 8.5, fig.height = 6.7, eval = F, echo = F}

# Samples were integrated to correct for batch effects. UMAPs are colored by sample identity or cell type.
# Load Seurat objects
sobjs <- rds_files %>%
  map(read_rds)

# Add orig.ident and cell_type to meta.data
sobjs <- sobjs %>%
  imap(AddMetaData, "orig.ident") %>%
  imap(~ {
    col_id <- .y %>%
      str_extract("[A-Z]+$") %>%
      str_c("cell_type", .)
    
    .x %>%
      FetchData(col_id) %>%
      AddMetaData(
        object   = .x,
        metadata = .,
        col.name = "cell_type"
      )
  })

# Merge objects and run PCA, UMAP, clustering
sobj <- sobjs %>%
  merge_sobj(sample_order = names(sobjs)) %>%
  cluster_RNA(resolution = 0.6) %>%
  AddMetaData(
    metadata = Embeddings(., reduction = "umap"),
    col.name = c("UMAP_1", "UMAP_2")
  )

# Integrate samples
sobj <- sobj %>%
  SplitObject(split.by = "orig.ident") %>%
  map(FindVariableFeatures) %>%
  FindIntegrationAnchors(dims = 1:40) %>%
  IntegrateData(dims = 1:40) %>%
  ScaleData(assay = "integrated") %>%
  cluster_RNA(
    assay      = "integrated",
    resolution = 1,
    features   = rownames(.),
    prefix     = "int_"
  ) %>%
  AddMetaData(
    metadata = Embeddings(., reduction = "int_umap"),
    col.name = c("int_UMAP_1", "int_UMAP_2")
  )

# Add cell type cluster column
sobj@meta.data <- sobj@meta.data %>%
  rownames_to_column("cell_id") %>%
  mutate(
    orig.ident = fct_relevel(orig.ident, names(sobjs)),
    sample_types = str_c(orig.ident, "-", cell_type)
  ) %>%
  column_to_rownames("cell_id")

# Prepare data for UMAPs
umap_data <- sobj %>%
  FetchData(c(
    "orig.ident", "cell_type",
    "UMAP_1",     "UMAP_2", 
    "int_UMAP_1", "int_UMAP_2",
    "integrated_clusters"
  )) %>%
  as_tibble(rownames = "cell_id") %>%
  pivot_longer(
    cols      = c(UMAP_1, UMAP_2, int_UMAP_1, int_UMAP_2), 
    names_to  = "UMAP_key", 
    values_to = "UMAP_coords"
  ) %>%
  mutate(
    UMAP_type = if_else(
      str_detect(UMAP_key, "^UMAP"), 
      "RNA",
      str_extract(UMAP_key, "^[a-zA-Z]+")
    ),
    UMAP_key = if_else(
      str_detect(UMAP_key, "^UMAP"),
      UMAP_key,
      str_remove(UMAP_key, "^[a-zA-Z]+_")
    ),
    UMAP_type = if_else(UMAP_type == "int", "Integrated", UMAP_type)
  ) %>%
  pivot_wider(names_from = UMAP_key, values_from = UMAP_coords)

# Create UMAPs
sam_umap <- umap_data %>%
  plot_features(
    feature = "orig.ident",
    split_id = "UMAP_type",
    plot_cols = theme_cols,
    feat_levels = names(sobjs),
    split_levels = c("RNA", "Integrated")
  ) +
  guides(color = col_guide) +
  blank_theme +
  theme(
    strip.background = element_blank(),
    strip.text       = element_text(size = 13),
    legend.title     = element_blank(),
    legend.text      = element_text(size = 10)
  )
  
type_umap <- umap_data %>%
  plot_features(
    feature = "cell_type",
    split_id = "UMAP_type",
    plot_cols = theme_cols,
    split_levels = c("RNA", "Integrated")
  ) +
  guides(color = guide_legend(ncol = 1, override.aes = list(size = 3.5))) +
  blank_theme +
  theme(
    strip.background = element_blank(),
    strip.text       = element_blank(),
    legend.title     = element_blank(),
    legend.text      = element_text(size = 10)
  )

# Create final figure
plot_grid(
  sam_umap, type_umap,
  nrow  = 2,
  align = "vh",
  axis  = "trbl"
)

```

