
```{r "{{.y}} Setup", echo = F}

rds_type <- "{{.x}}"
rds_name <- "{{.y}}"
rds_file <- str_c(rds_name, "_so.rds")

sobj <- read_rds(file.path(params$rds_dir, rds_file))

cell_type_id <- str_c("cell_type", rds_type)
cluster_id <- str_c("cell_type", rds_type, "2")

sobj@meta.data <- sobj@meta.data %>%
  rownames_to_column("cell_id") %>%
  mutate(!!sym(cell_type_id) := str_remove(!!sym(cluster_id), "^[0-9]+-")) %>%
  column_to_rownames("cell_id")

```

## **`r rds_file`**

### Cell type markers

Ovalbumin signal is shown for each cell type.
```{r "{{.y}} Cell type OVA", fig.width = 6, fig.height = 4}

# Set cell type order and colors
cell_types <- sobj@meta.data %>%
  pull(!!sym(cell_type_id)) %>%
  unique()

names(cell_types) <- cell_types

type_cols <- theme_cols
names(type_cols) <- cell_types
type_cols <- type_cols[!is.na(names(type_cols))]

# Plot OVA counts
ova_data <- sobj %>%
  FetchData(c("adt_ovalbumin", cell_type_id, cluster_id)) %>%
  as_tibble(rownames = "cell_id") %>%
  mutate(!!sym(cell_type_id) := fct_reorder(!!sym(cell_type_id), adt_ovalbumin, median))
  
ova_data %>%
  ggplot(aes(!!sym(cell_type_id), adt_ovalbumin, color = !!sym(cell_type_id))) +
  geom_quasirandom(size = 0.5) +
  scale_color_manual(values = type_cols) +
  scale_y_log10() +
  coord_flip() +
  theme_info +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 13),
    axis.text    = element_text(size = 10)
  )

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all cell types. Gene expression signal is shown for the top maker genes for each cell type (top, middle). GO terms were identified for marker genes, the top 8 terms are labeled (bottom).
```{r "{{.y}} Cell type markers", fig.width = 8.5, fig.height = 13, results = "asis"}

# Find all cell type markers
Idents(sobj) <- sobj %>%
  FetchData(cell_type_id)

all_type_marks <- sobj %>%
  FindAllMarkers(only.pos = T) %>%
  as_tibble() %>%
  filter(p_val_adj < 0.05)

# Cell type UMAP
type_umap <- sobj %>%
  plot_features(
    feature     = cell_type_id,
    plot_cols   = type_cols,
    feat_levels = names(type_cols)
  ) +
  guides(color = col_guide) +
  blank_theme +
  theme(
    legend.position = "top",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 10)
  )

# Marker plots
for (i in seq_along(type_cols)) {
  cat("\n#### ", names(type_cols[i]), "\n", sep = "")

  type_marks <- all_type_marks %>%
    filter(cluster == names(type_cols[i]))

  type_marks_fig <- sobj %>%
    create_marker_fig(
      input_markers = type_marks,
      type_id       = cell_type_id,
      input_umap    = type_umap,
      umap_color    = type_cols[[i]],
      box_colors    = type_cols
    )

  print(type_marks_fig)
  cat("\n\n---\n\n<br>\n\n<br>\n\n")
}

```

### Cluster markers

Ovalbumin signal is shown for each cluster.
```{r "{{.y}} Cluster OVA", fig.width = 6, fig.height = 4}

# Set cluster order and colors
cell_clusts <- sobj@meta.data %>%
  mutate(
    type_clust = str_extract(!!sym(cluster_id), "^[0-9]+"),
    type_clust = as.numeric(type_clust)
  ) %>%
  arrange(!!sym(cell_type_id), type_clust) %>%
  pull(!!sym(cluster_id)) %>%
  unique()

names(cell_clusts) <- cell_clusts

clust_cols <- theme_cols
names(clust_cols) <- cell_clusts
clust_cols <- clust_cols[!is.na(names(clust_cols))]

# Plot OVA counts
ova_data <- sobj %>%
  FetchData(c("adt_ovalbumin", cell_type_id, cluster_id)) %>%
  as_tibble(rownames = "cell_id") %>%
  mutate(!!sym(cluster_id) := fct_reorder(!!sym(cluster_id), adt_ovalbumin, median))
  
ova_data %>%
  ggplot(aes(!!sym(cluster_id), adt_ovalbumin, color = !!sym(cluster_id))) +
  geom_quasirandom(size = 0.5) +
  scale_color_manual(values = clust_cols) +
  scale_y_log10() +
  coord_flip() +
  theme_info +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 13),
    axis.text    = element_text(size = 10)
  )

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all clusters. Gene expression signal is shown for the top maker genes for each cluster (top, middle). GO terms were identified for marker genes, the top 8 terms are labeled (bottom).
```{r "{{.y}} Cluster markers", fig.width = 8.5, fig.height = 13, results = "asis"}

# Find all cell cluster markers
Idents(sobj) <- sobj %>%
  FetchData(cluster_id)

all_clust_marks <- sobj %>%
  FindAllMarkers(only.pos = T) %>%
  as_tibble() %>%
  filter(p_val_adj < 0.05)

# Cluster UMAP
clust_umap <- sobj %>%
  plot_features(
    feature     = cluster_id,
    plot_cols   = clust_cols,
    feat_levels = names(clust_cols)
  ) +
  guides(color = col_guide) +
  blank_theme +
  theme(
    legend.position = "top",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 10)
  )

# Cluster plots
for (i in seq_along(clust_cols)) {
  cat("\n#### ", names(clust_cols[i]), "\n", sep = "")

  clust_marks <- all_clust_marks %>%
    filter(cluster == names(clust_cols[i]))
  
  clust_marks_fig <- sobj %>%
    create_marker_fig(
      input_markers = clust_marks,
      type_id       = cluster_id,
      input_umap    = clust_umap,
      umap_color    = clust_cols[[i]],
      box_colors    = clust_cols
    )

  print(clust_marks_fig)
  cat("\n\n---\n\n<br>\n\n<br>\n\n")
}

```

### Cell type cluster markers

Ovalbumin signal is shown for each cell type cluster.
```{r "{{.y}} Cell type cluster OVA", fig.width = 6, fig.height = 4}

# Plot OVA counts
ova_data <- sobj %>%
  FetchData(c("adt_ovalbumin", cell_type_id, cluster_id)) %>%
  as_tibble(rownames = "cell_id") %>%
  group_by(!!sym(cell_type_id)) %>%
  mutate(type_med = median(adt_ovalbumin)) %>%
  group_by(!!sym(cluster_id)) %>%
  mutate(clust_med = median(adt_ovalbumin)) %>%
  ungroup() %>%
  arrange(type_med, clust_med) %>%
  mutate(!!sym(cluster_id) := fct_inorder(!!sym(cluster_id)))
  
ova_data %>%
  ggplot(aes(!!sym(cluster_id), adt_ovalbumin, color = !!sym(cluster_id))) +
  geom_quasirandom(size = 0.5) +
  scale_color_manual(values = clust_cols) +
  scale_y_log10() +
  coord_flip() +
  theme_info +
  theme(
    strip.text = element_blank(),
    legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 13),
    axis.text    = element_text(size = 10)
  )

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by splitting the cells based on cell type and comparing the clusters for each cell type. Gene expression signal is shown for the top maker genes for each cell type cluster (top, middle). GO terms were identified for marker genes, the top 8 terms are labeled (bottom).
```{r "{{.y}} Cell type cluster markers", fig.width = 8.5, fig.height = 13, results = "asis"}

# Find cluster markers separately for each cell type
sep_clust_marks <- cell_types %>%
  map(~ {
    find_sep_clust_markers(
      input_type = .x,
      input_sobj = sobj,
      type_col   = cell_type_id,
      clust_col  = cluster_id
    )
  }) %>%
  compact() %>%
  bind_rows()

# Set cluster order
sep_clusts <- unique(sep_clust_marks$cluster)
sep_clusts <- clust_cols[names(clust_cols) %in% sep_clusts] %>%
  names()

# Cluster plots
for (i in seq_along(sep_clusts)) {
  cat("\n#### ", sep_clusts[i], "\n", sep = "")
  
  sep_marks <- sep_clust_marks %>%
    filter(cluster == sep_clusts[i])

  type <- sep_clusts[i] %>%
    str_remove("^[0-9]+-")
  
  regex_type <- str_c("-", type) %>%
    str_replace("\\+", "\\\\+")
  
  sep_cols <- clust_cols[grepl(regex_type, names(clust_cols))]
  sep_cols <- c( "Other" = "#f0f0f0", sep_cols)
  
  sep_clust_umap <- sobj %>%
    FetchData(c("UMAP_1", "UMAP_2", cell_type_id, cluster_id)) %>%
    as_tibble(rownames = "cell_id") %>%
    mutate(!!sym(cluster_id) := if_else(!!sym(cell_type_id) != type, "Other", !!sym(cluster_id))) %>%
    plot_features(
      feature     = cluster_id,
      plot_cols   = sep_cols,
      feat_levels = names(sep_cols)
    ) +
    guides(color = col_guide) +
    blank_theme +
    theme(
      legend.position = "top",
      legend.title    = element_blank(),
      legend.text     = element_text(size = 10)
    )
  
  sep_clust_marks_fig <- sobj %>%
    create_marker_fig(
      input_markers = sep_marks,
      type_id       = cluster_id,
      input_umap    = sep_clust_umap,
      umap_color    = sep_cols[sep_clusts[i]],
      box_colors    = sep_cols,
      cell_type     = type
    )
  
  print(sep_clust_marks_fig)
  cat("\n\n---\n\n<br>\n\n<br>\n\n")
}

```

### Ovalbumin markers

Cells were divided into 6 groups based on ovalbumin signal. The proportion of cell types and cell clusters that make up each group is shown below. 
```{r "{{.y}} OVA cluster summary", fig.width = 8.5, fig.height = 5}

# Set OVA colors
ova_cols <- theme_cols[c(1:5, 9)]
names(ova_cols) <- as.character(1:6)

# Divide cells based on OVA signal
sobj <- sobj %>%
  FetchData("adt_ovalbumin") %>%
  rownames_to_column("cell_id") %>%
  mutate(
    ova_group = ntile(adt_ovalbumin, 6),
    ova_group = as.character(ova_group)
  ) %>%
  column_to_rownames("cell_id") %>%
  AddMetaData(
    object = sobj,
    metadata = .
  )

# OVA boxplots
ova_boxes <- sobj@meta.data %>%
  ggplot(aes(ova_group, adt_ovalbumin, color = ova_group)) +
  geom_quasirandom(size = 0.5) +
  scale_color_manual(values = ova_cols) +
  scale_y_log10() +
  theme_info +
  theme(
    legend.position = "none",
    legend.title    = element_text(size = 13),
    legend.text     = element_text(size = 8),
    axis.title      = element_text(size = 13),
    axis.text       = element_text(size = 8)
  )

# OVA cell type bar graphs
type_bar <- sobj %>%
  plot_cell_count(
    group_id = "ova_group",
    split_id = NULL,
    fill_id = cell_type_id,
    plot_colors = type_cols
  ) +
  labs(x = "ova_group") +
  guides(fill = guide_legend(ncol = 1)) +
  theme(
    legend.position = "bottom",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 8),
    axis.title.x    = element_text(size = 13),
    axis.text       = element_text(size = 8),
  )

# OVA cluster bar graphs
clust_bar <- sobj %>%
  plot_cell_count(
    group_id = "ova_group",
    split_id = NULL,
    fill_id = cluster_id,
    plot_colors = clust_cols
  ) +
  labs(x = "ova_group") +
  guides(fill = guide_legend(ncol = 2)) +
  theme(
    legend.position = "bottom",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 8),
    axis.title      = element_text(size = 13),
    axis.text.x     = element_text(size = 8),
    axis.title.y    = element_blank(),
    axis.text.y     = element_blank(),
    axis.ticks.y    = element_blank(),
    axis.line.y     = element_blank()
  )

# Create final figure
plot_grid(
  ova_boxes, type_bar, clust_bar,
  rel_widths = c(0.38, 0.365, 0.305),
  nrow  = 1,
  align = "h",
  axis  = "tb"
)

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all ovalbumin groups. Gene expression signal is shown for the top maker genes for each group (top, middle). GO terms were identified for marker genes, the top 8 terms are labeled (bottom).
```{r "{{.y}} OVA cluster markers", fig.width = 8.5, fig.height = 13, results = "asis"}

# OVA markers
Idents(sobj) <- sobj %>%
  FetchData("ova_group")

ova_markers <- sobj %>%
  FindAllMarkers(only.pos = T) %>%
  as_tibble() %>%
  filter(p_val_adj < 0.05)

# OVA cluster plots
for (i in seq_along(ova_cols)) {
  cat("\n#### ova_group-", names(ova_cols[i]), "\n", sep = "")
  
  umap_levels <- ova_cols[ova_cols != ova_cols[i]]
  umap_levels <- c(umap_levels, ova_cols[i]) %>%
    names()
  
  # OVA groups UMAP
  ova_umap <- sobj %>%
    plot_features(
      feature     = "ova_group",
      plot_cols   = ova_cols,
      feat_levels = umap_levels
    ) +
    guides(color = col_guide) +
    blank_theme +
    theme(
      legend.position = "top",
      legend.title    = element_blank(),
      legend.text     = element_text(size = 10)
    )

  # OVA figure
  ova_marks <- ova_markers %>%
    filter(cluster == names(ova_cols[i]))
  
  ova_marks_fig <- sobj %>%
    create_marker_fig(
      input_markers = ova_marks,
      type_id       = "ova_group",
      input_umap    = ova_umap,
      umap_color    = ova_cols[[i]],
      box_colors    = ova_cols
    )

  print(ova_marks_fig)
  cat("\n\n---\n\n<br>\n\n<br>\n\n")
}
  
```

```{r, eval = F, echo = F}

x <- GO_list %>%
  compact() %>%
  bind_rows()

top_terms <- x %>%
  filter(source == "GO:BP") %>%
  group_by(cluster) %>%
  top_n(10, desc(p_value)) %>%
  ungroup() %>%
  pull(term_name) %>%
  unique()

# all_terms <- unique(x$term_name)
# all_terms <- all_terms[!all_terms %in% top_terms]

GO_ova_data <- top_terms %>%
  map(~ {
    clusts <- x %>%
      filter(
        source == "GO:BP",
        term_name == .x
      ) %>%
      pull(cluster)
    
    ova_counts <- sobj %>%
      FetchData(c(cluster_id, "adt_ovalbumin")) %>%
      as_tibble(rownames = "cell_id") %>%
      filter(!!sym(cluster_id) %in% clusts) %>%
      mutate(term_name = .x)
  }) %>%
  compact() %>%
  bind_rows()

GO_box_data <- GO_ova_data %>%
  group_by(term_name) %>%
  mutate(
    med_ova = median(adt_ovalbumin),
    up_qt = quantile(adt_ovalbumin)[4]
  ) %>%
  ungroup() %>%
  mutate(term_name = fct_reorder(term_name, adt_ovalbumin, median))

y_max <- max(GO_box_data$up_qt) * 1.1

GO_box_data %>%
  ggplot(aes(term_name, adt_ovalbumin, fill = med_ova)) +
  geom_boxplot(size = 0.1, color = "white", outlier.shape = NA) +
  coord_flip(ylim = c(0, y_max)) +
  theme_info +
  theme(
    legend.position = "none",
    axis.title.y    = element_blank(),
    axis.text       = element_text(size = 8)
  )

  # arrange(med_ova) %>%
  # tail(10) %>%
  # mutate(term_name = fct_inorder(term_name)) %>%

```


