
```{r "{{.x}} Setup", echo = F}

# Load Seurat object
so_name   <- "{{.x}}"
so_type   <- so_types[so_name]
so_title  <- so_titles[so_name]
type_cols <- so_cols[[so_name]]
sobj      <- sobjs[[so_name]]
xlsx_name <- here(params$xlsx_dir)
xlsx_path <- NULL

mtplyr_1 <- if_else(ncol(sobj) < 500, 3, 1)
mtplyr_2 <- if_else(ncol(sobj) < 500, 6, 1)
mtplyr_3 <- if_else(ncol(sobj) < 750, mtplyr_2 * 2.5, 1)

# Format meta.data and add pseudo count
subtype_column <- "subtype"
clust_column   <- "subtype_cluster"
data_column    <- c("Relative ova signal" = "ova_fc")

sobj@meta.data <- sobj@meta.data %>%
  rownames_to_column("cell_id") %>%
  rename(
    subtype = !!sym(subtype_column),
    subtype_cluster = !!sym(clust_column)
  ) %>%
  column_to_rownames("cell_id")

# Get vector of cell types
subtypes <- sobj@meta.data %>%
  pull(subtype) %>%
  unique() %>%
  setNames(., .)

# Section descriptions
marker_desc <- "Gene expression signal is shown for the top marker genes (top, middle)."
GO_desc <- "GO terms were identified for marker genes, the top terms are labeled, the size of each point indicates the number of overlapping genes (bottom)."

# Evaluate chunks for subtype ovalbumin markers?
# d2_FRC has too few cells in each subtype, throws normalmixEM error
eval_subtype_ova <- so_name != "d2_FRC"

```

## `r so_title`

### Subtype Markers

A UMAP projection colored by subtype is shown on the left and ovalbumin signal for each subtype is shown on the right.
```{r "{{.x}} Subtype summary", fig.width = 9, fig.height = 4.5}

# Subtype UMAP
type_umap <- sobj %>%
  plot_features(
    feature     = "subtype",
    pt_size     = 0.1 * mtplyr_3,
    pt_outline  = 0.1 * mtplyr_3 + 0.3,
    plot_cols   = type_cols,
    feat_levels = names(type_cols)
  ) +
  guides(color = guide_legend(override.aes = list(size = 3.5), nrow = 3)) +
  blank_theme +
  theme(legend.position = "none")

# OVA boxes
box_data <- sobj@meta.data %>%
  as_tibble(rownames = "cell_id") %>%
  mutate(subtype = fct_reorder(subtype, !!sym(data_column), median))

type_order    <- levels(box_data$subtype)
control_types <- c("B Cell", "T Cell")
control_types <- control_types[control_types %in% type_order]
type_order    <- type_order[!type_order %in% control_types]
type_order    <- c(control_types, type_order)

ova_boxes <- box_data %>%
  mutate(subtype = fct_relevel(subtype, type_order)) %>%
  ggplot(aes(!!sym(data_column), subtype, fill = subtype)) +
  geom_violin(size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
  stat_summary(geom = "point", color = "black", fun = median) +
  scale_x_log10(labels = trans_format("log10", math_format(10^.x)), breaks = c(0.01, 1, 100, 10000)) +
  scale_fill_manual(values = type_cols) +
  labs(x = names(data_column)) +
  theme_minimal_vgrid() +
  theme(
    legend.position    = "none",
    axis.title.y       = element_blank(),
    axis.title         = element_text(size = 10),
    axis.text          = element_text(size = 10),
    axis.line.y        = element_line(color = "black"),
    axis.ticks.x       = element_line(size = 0.1),
    axis.ticks.y       = element_line(color = "black"),
    panel.grid.major.x = element_line(size = 0.1)
  )

# Create final figure
plot_grid(
  type_umap, ova_boxes,
  rel_widths = c(0.46, 0.54),
  nrow  = 1,
  align = "h",
  axis  = "trbl"
)

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all subtypes. `r marker_desc` `r GO_desc`
```{r "{{.x}} Subtype markers", fig.width = 8.5, fig.height = 14, results = "asis"}

# Create figures
if (!is_empty(xlsx_name)) {
  xlsx_path <- xlsx_name %>%
    str_c("/", so_name, "_subtype")
}

create_marker_panel_v1(
  input_sobj   = sobj,
  input_cols   = type_cols,
  clust_column = "subtype",
  xlsx_name    = xlsx_path,
  n_boxes      = 18,
  all_boxes    = T,
  color_guide  = outline_guide,
  strip.text   = element_text(size = 11)
)

```

### Cluster Markers

A UMAP projection colored by cell cluster is shown on the left and ovalbumin signal for each cluster is shown on the right.
```{r "{{.x}} Cluster summary", fig.width = 9, fig.height = 4.2}

# Set cluster order and colors
cell_clusts <- sobj@meta.data %>%
  pull(subtype_cluster) %>%
  unique() %>%
  setNames(., .)

clust_cols <- get_cols(length(cell_clusts)) %>%
  setNames(., cell_clusts)

# Cluster UMAP
clust_umap <- sobj %>%
  plot_features(
    feature     = "subtype_cluster",
    pt_size     = 0.1 * mtplyr_3,
    pt_outline  = 0.1 * mtplyr_3 + 0.3,
    plot_cols   = clust_cols,
    feat_levels = names(clust_cols),
  ) +
  guides(color = guide_legend(override.aes = list(size = 3.5), nrow = 10)) +
  blank_theme +
  theme(legend.position = "none")

# OVA boxes
ova_boxes <- sobj %>%
  FetchData(c(data_column, "cell_type", "subtype_cluster")) %>%
  as_tibble(rownames = "cell_id") %>%
  group_by(subtype_cluster) %>%
  filter(n_distinct(cell_id) > 10) %>%
  ungroup() %>%
  mutate(subtype_cluster = fct_reorder(subtype_cluster, !!sym(data_column), median)) %>%
  ggplot(aes(!!sym(data_column), subtype_cluster, fill = subtype_cluster)) +
  geom_violin(size = 0.3, draw_quantiles = c(0.25, 0.75), alpha = 0.75) +
  stat_summary(geom = "point", color = "black", fun = median) +
  scale_x_log10(labels = trans_format("log10", math_format(10^.x)), breaks = c(0.01, 1, 100, 10000)) +
  scale_fill_manual(values = clust_cols) +
  labs(x = names(data_column)) +
  theme_minimal_vgrid() +
  theme(
    legend.position    = "none",
    axis.title.y       = element_blank(),
    axis.title         = element_text(size = 10),
    axis.text          = element_text(size = 10),
    axis.line.y        = element_line(color = "black"),
    axis.ticks.x       = element_line(size = 0.1),
    axis.ticks.y       = element_line(color = "black"),
    panel.grid.major.x = element_line(size = 0.1)
  )

# Create final figure
plot_grid(
  clust_umap, ova_boxes,
  rel_widths = c(0.44, 0.56),
  nrow  = 1,
  align = "h",
  axis  = "trbl"
)

```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all clusters. `r marker_desc` `r GO_desc`
```{r "{{.x}} Cluster markers", fig.width = 8.5, fig.height = 14, results = "asis"}

# Create figures
if (!is_empty(xlsx_name)) {
  xlsx_path <- xlsx_name %>%
    str_c("/", so_name, "_cluster")
}

create_marker_panel_v1(
  input_sobj   = sobj,
  input_cols   = clust_cols,
  clust_column = "subtype_cluster",
  xlsx_name    = xlsx_path,
  n_boxes      = 12,
  all_boxes    = T,
  median_pt    = 0.5,
  color_guide  = outline_guide,
  strip.text   = element_text(size = 11)
)

```

### Ovalbumin Markers

Cells were divided into groups based on ovalbumin signal. The ovalbumin groups are shown on the left and ovalbumin signal is shown on the right. The proportion of subtypes and cell clusters that make up each group is shown at the bottom.
```{r "{{.x}} OVA groups summary 1", include = F}

# OVA group UMAP
ova_grp_umap <- sobj %>%
  plot_features(
    feature     = "GMM_grp",
    pt_size     = 0.1 * mtplyr_3,
    pt_outline  = 0.1 * mtplyr_3 + 0.3,
    plot_cols   = ova_cols,
    feat_levels = names(ova_cols)
  ) +
  guides(color = outline_guide) +
  ggtitle("Ovalbumin Group") +
  blank_theme +
  theme(
    plot.title   = element_text(size = 13),
    legend.title = element_blank(),
    legend.text  = element_text(size = 8)
  )

# OVA UMAP
ova_umap <- sobj %>%
  plot_features(
    feature    = "adt_ovalbumin",
    data_slot  = "counts",
    plot_cols  = c("#ffffff", ova_cols["ova high"]),
    pt_size    = 0.1 * mtplyr_3,
    pt_outline = 0.1 * mtplyr_3 + 0.3,
    min_pct    = 0.01,
    max_pct    = 0.99
  ) +
  ggtitle("adt_ovalbumin") +
  blank_theme +
  theme(
    plot.title        = element_text(size = 13),
    legend.key.width  = unit(0.1, "cm"),
    legend.key.height = unit(0.3, "cm"),
    legend.title      = element_blank(),
    legend.text       = element_text(size = 8)
  )

# OVA hist
text_theme <- theme(
  axis.title  = element_text(size = 10),
  legend.text = element_text(size = 8),
  axis.text   = element_text(size = 8)
)

ova_hist <- sobj@meta.data %>%
  filter(GMM_grp != "Other") %>%
  mutate(GMM_grp = fct_relevel(GMM_grp, c("ova low", "ova high"))) %>%
  ggplot(aes(adt_ovalbumin + 1, after_stat(density), fill = GMM_grp)) +
  
  stat_density(geom = "point", position = "identity", size = 0, color = "white") +
  geom_density(fill = "white", color = "white", size = 0.3, alpha = 0.9) +
  geom_density(size = 0.3, alpha = 0.8, show.legend = F) +
  
  geom_vline(aes(xintercept = mu), size = 0.5, linetype = 2, color = "grey35") +
  coord_cartesian(ylim = c(0, 1.7)) +
  scale_fill_manual(values = ova_cols) +
  scale_x_log10(labels = trans_format("log10", math_format(10^.x))) +
  labs(x = "ova counts", y = "Density") +
  guides(fill = guide_legend(override.aes = list(shape = 22, size = 3.5, stroke = 0.25, color = "black"))) +
  theme_minimal_hgrid() +
  text_theme +
  theme(
    plot.margin        = unit(c(0.2, 0.5, 0.2, 0.2), "cm"),
    legend.position    = c(0.05, 0.92),
    legend.key.height  = unit(0.15, "cm"),
    legend.title       = element_blank(),
    axis.line.y        = element_line(size = 0.5, color = "grey85"),
    axis.ticks.y       = element_line(size = 0.1),
    panel.grid.major.y = element_line(size = 0.1)
  )

# OVA subtype bar graphs
type_bar <- sobj@meta.data %>%
  as_tibble(rownames = "cell_id") %>%
  mutate(
    subtype = fct_reorder(subtype, cell_id, n_distinct),
    GMM_grp = fct_relevel(GMM_grp, c("ova low", "ova high", "Other"))
  ) %>%
  ggplot(aes(GMM_grp, fill = subtype)) +
  
  stat_count(position = "fill", geom = "point", size = 0, color = "white") +
  geom_bar(position = "fill", size = 0.25, color = "black", show.legend = F) +
  
  scale_fill_manual(values = type_cols) +
  scale_y_continuous(breaks = c(0, 0.5, 1)) +
  guides(fill = guide_legend(ncol = 1, override.aes = list(shape = 22, size = 3.5, stroke = 0.25, color = "black"))) +
  labs(y = "Fraction of cells") +
  theme_minimal_hgrid() +
  text_theme +
  theme(
    legend.title       = element_blank(),
    legend.key.height  = unit(0.35, "cm"),
    axis.title.x       = element_blank(),
    axis.line.y        = element_line(size = 0.5, color = "grey85"),
    axis.ticks.y       = element_line(size = 0.1),
    panel.grid.major.y = element_blank()
  )

# Create final figure
umaps <- plot_grid(
  ova_grp_umap, ova_umap,
  nrow  = 1,
  align = "hv",
  axis  = "trbl"
)

bars <- plot_grid(
  ova_hist, type_bar,
  nrow  = 1,
  align = "h",
  axis  = "tb"
)

ova_fig <- plot_grid(
  umaps, bars,
  nrow = 2,
  align = "vh",
  axis  = "trbl"
)

```

```{r, ref.label = "{{.x}} OVA groups summary 1", eval = F}
# Divide into two chunks to omit GMM messages
```

```{r "{{.x}} OVA groups summary 2", fig.width = 8, fig.height = 7, echo = F}
ova_fig
```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all ovalbumin groups. `r marker_desc` `r GO_desc`
```{r "{{.x}} OVA groups markers", fig.width = 8.5, fig.height = 14, results = "asis"}

# Create figures
if (!is_empty(xlsx_name)) {
  xlsx_path <- xlsx_name %>%
    str_c("/", so_name, "_ova")
}

create_marker_panel_v1(
  input_sobj      = sobj,
  input_cols      = ova_cols,
  clust_column    = "GMM_grp",
  exclude_clust   = "Other",
  xlsx_name       = xlsx_path,
  n_boxes         = 34,
  all_violins     = T,
  order_boxes     = F,
  color_guide     = outline_guide,
  panel.spacing.y = unit(0, "cm"),
  strip.text      = element_text(size = 10, angle = 90, hjust = 0)
)

```

### Subtype Ovalbumin Markers

Each subtype was divided into groups based on ovalbumin signal. A UMAP projection colored by the subtype ovalbumin groups is shown on the left and ovalbumin signal is shown on the right.
```{r "{{.x}} Subtype OVA groups summary 1", include = F, eval = eval_subtype_ova}

# Use GMM to divide subtypes based on OVA signal
GMM_res <- subtypes %>%
  map(~ {
    classify_ova(
      sobj_in     = sobj,
      filt_column = "subtype",
      filt        = .x,
      data_column = "adt_ovalbumin",
      data_slot   = "counts",
      quiet       = T,
      return_sobj = F
    )
  }) %>%
  bind_rows() %>%
  mutate(type_GMM_grp_2 = str_c(subtype, "-", GMM_grp)) %>%
  select(
    cell_id,
    type_GMM_grp = GMM_grp,
    type_GMM_grp_2,
    type_mu = mu
  ) %>%
  column_to_rownames("cell_id")

# Add OVA groups to meta.data
sobj <- sobj %>%
  AddMetaData(GMM_res)

type_ova_cols <- type_cols %>%
  map(~ c(.x, darken(.x, 0.3))) %>%
  unlist()

names(type_ova_cols) <- names(type_cols) %>%
  map(~ str_c(.x, "-", names(ova_cols[2:1]))) %>%
  unlist()

# OVA group UMAP
ova_grp_umap <- sobj %>%
  plot_features(
    feature     = "type_GMM_grp_2",
    pt_size     = 0.1 * mtplyr_3,
    pt_outline  = 0.1 * mtplyr_3 + 0.3,
    plot_cols   = type_ova_cols,
    feat_levels = names(type_ova_cols)
  ) +
  guides(color = guide_legend(override.aes = list(size = 3.5, shape = 21, stroke = 0.25, color = "black"), nrow = 10)) +
  blank_theme +
  theme(
    legend.position = "bottom",
    legend.title    = element_blank(),
    legend.text     = element_text(size = 8)
  )

# OVA boxes
box_data <- sobj@meta.data %>%
  as_tibble(rownames = "cell_id") %>%
  group_by(subtype) %>%
  mutate(type_med = median(!!sym(data_column))) %>%
  group_by(type_GMM_grp_2) %>%
  mutate(clust_med = median(!!sym(data_column))) %>%
  ungroup() %>%
  arrange(type_med, clust_med) %>%
  mutate(
    subtype = fct_inorder(subtype),
    type_GMM_grp_2 = fct_inorder(type_GMM_grp_2)
  )

type_order    <- levels(box_data$subtype)
control_types <- c("B Cell", "T Cell")
control_types <- control_types[control_types %in% type_order]
type_order    <- type_order[!type_order %in% control_types]
type_order    <- c(control_types, type_order)

ova_boxes <- box_data %>%
  mutate(subtype = fct_relevel(subtype, type_order)) %>%
  ggplot(aes(subtype, !!sym(data_column), color = type_GMM_grp_2)) +
  geom_quasirandom(size = 0.25 * mtplyr_2) +
  scale_y_log10(labels = trans_format("log10", math_format(10 ^ .x))) +
  coord_flip() +
  scale_color_manual(values = type_ova_cols) +
  labs(y = names(data_column)) +
  theme_minimal_vgrid() +
  theme(
    legend.position    = "none",
    axis.title.y       = element_blank(),
    axis.title         = element_text(size = 10),
    axis.text          = element_text(size = 10),
    axis.line.y        = element_line(color = "black"),
    axis.ticks.x       = element_line(size = 0.1),
    axis.ticks.y       = element_line(color = "black"),
    panel.grid.major.x = element_line(size = 0.1)
  )
  
# Create final figure
ova_fig <- plot_grid(
  ova_grp_umap, ova_boxes,
  rel_widths = c(0.44, 0.56),
  nrow  = 1,
  align = "h",
  axis  = "trbl"
)

```

```{r, ref.label = "{{.x}} Subtype OVA groups summary 1", eval = F}
# Divide into two chunks to omit GMM messages
```

```{r "{{.x}} Subtype OVA groups summary 2", fig.width = 8.5, fig.height = 6, echo = F, eval = eval_subtype_ova}
ova_fig
```

<br>

### {.tabset .tabset-pills}

Marker genes were identified by comparing all ovalbumin groups together. `r marker_desc` `r GO_desc`
```{r "{{.x}} Subtype OVA markers 1", fig.width = 8.5, fig.height = 14, results = "asis", eval = eval_subtype_ova}

# Create figures
if (!is_empty(xlsx_name)) {
  xlsx_path <- xlsx_name %>%
    str_c("/", so_name, "_subtype_ova_1")
}

create_marker_panel_v1(
  input_sobj      = sobj,
  input_cols      = type_ova_cols,
  clust_column    = "type_GMM_grp_2",
  xlsx_name       = xlsx_path,
  n_boxes         = 16,
  all_boxes       = T,
  median_pt       = 0.5,
  color_guide     = outline_guide,
  panel.spacing.y = unit(0, "cm"),
  strip.text      = element_text(size = 10, angle = 90, hjust = 0)
)

```

### {.tabset .tabset-pills}

Marker genes were identified by splitting cells based on subtype and comparing the ovalbumin groups within the subtype. `r marker_desc` `r GO_desc`
```{r "{{.x}} Subtype OVA markers 2", fig.width = 8.5, fig.height = 14, results = "asis", eval = eval_subtype_ova}

# Find OVA markers separately for each OVA group
fig_markers <- subtypes %>%
  map(~ {
    find_group_markers(
      input_grp  = .x,
      input_sobj = sobj,
      grp_col    = "subtype",
      clust_col  = "type_GMM_grp_2"
    )
  }) %>%
  compact() %>%
  bind_rows()

# Create figures
if (!is_empty(xlsx_name)) {
  xlsx_path <- xlsx_name %>%
    str_c("/", so_name, "_subtype_ova_2")
}

create_marker_panel_v2(
  input_sobj      = sobj,
  input_markers   = fig_markers,
  input_cols      = type_ova_cols,
  grp_column      = "subtype",
  clust_column    = "type_GMM_grp_2",
  xlsx_name       = xlsx_path,
  n_boxes         = 34,
  all_violins     = T,
  order_boxes     = F,
  color_guide     = outline_guide,
  panel.spacing.y = unit(0, "cm"),
  strip.text      = element_text(size = 10, angle = 90, hjust = 0)
)

```



```{r "{{.x}} TEST", eval = F, echo = F}

group_column <- "type_ova_grp"

res <- sobj %>%
  wilcoxauc(group_by = group_column) %>%
  as_tibble() %>%
  filter(
    padj    < params$p_max_markers,
    logFC   > params$FC_min,
    auc     > params$auc_min,
    pct_in  > params$pct_in_min,
    pct_out < params$pct_out_max
  ) %>%
  arrange(desc(logFC))

res <- res %>%
  group_by(feature) %>%
  filter(n() == 1) %>%
  ungroup()

x <- res %>% 
  group_by(feature) %>% 
  filter(group == "high-cDC2 Tbet-") %>% 
  head() %>% 
  pull(feature)

sobj %>% 
  subset(type_ova_grp == "high-cDC2 Tbet-") %>% 
  FetchData(x) %>% 
  as_tibble(rownames = "cell_id") %>% 
  pivot_longer(cols = -cell_id, names_to = "key", values_to = "value") %>% 
  mutate(key = fct_reorder(key, value, median)) %>% 
  ggplot(aes(key, value, color = key)) + 
  geom_boxplot() + 
  theme_info

# unique(marks$group)[1:4] %>%
#   map(~ {
#     marks_in <- marks %>%
#       filter(group == .x) %>%
#       pull(feature)
#     
#     if (!is_empty(marks_in)) {
#       create_marker_boxes(
#         input_sobj = sobj,
#         input_markers = marks_in,
#         clust_column = "type_ova_grp",
#         box_cols = type_ova_cols
#         # n_boxes          = 16,
#         # all_violins      = T,
#         # order_boxes      = T,
#         # panel.background = element_rect(color = "#fafafa", fill = "#fafafa"),
#         # panel.spacing.y  = unit(0, "cm"),
#         # panel.spacing.x  = unit(0.2, "cm"),
#         # strip.text       = element_text(size = 10, angle = 90, hjust = 0)
#       )
#     }
#   })

```

```{r "{{.x}} CELL CYCLE", eval = F, echo = F}

s.genes <- cc.genes$s.genes %>%
  str_to_title()

g2m.genes <- cc.genes$g2m.genes %>%
  str_to_title()

so_in <- sobjs[[2]]

so_in <- so_in %>%
  CellCycleScoring(
    s.features = s.genes, 
    g2m.features = g2m.genes,
    set.ident = T
  )

so_in %>%
  plot_features(
    feature = "Phase",
    pt_size = 1
  )

```